### 2018-05-24 mycv/cv/images.tex
tex files were added

\batchmode

\documentclass[11pt,a4paper]{awesome-cv}

\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

\fontdir[fonts/]

\colorlet{awesome}{awesome-red}

\setbool{acvSectionColorHighlight}{true}

%
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\name{Youngung}{Jeong}
\position{Assistant professor}
\address{20 Changwondaehak-ro, Changwon, Gyeongnam, 51140, Republic of Korea}

\mobile{(+82) 10-9763-3022}
\email{yjeong@changwon.ac.kr}
\homepage{52-208}
\github{youngung}
\gitlab{youngung.jeong}

\usepackage[dvips]{color}

\pagecolor[gray]{.7}

\usepackage[]{inputenc}

\makeatletter

\makeatletter
\count@=\the\catcode`\_ \catcode`\_=8 
\newenvironment{tex2html_wrap}{}{}%
\catcode`\<=12\catcode`\_=\count@
\newcommand{\providedcommand}[1]{\expandafter\providecommand\csname #1\endcsname}%
\newcommand{\renewedcommand}[1]{\expandafter\providecommand\csname #1\endcsname{}%
  \expandafter\renewcommand\csname #1\endcsname}%
\newcommand{\newedenvironment}[1]{\newenvironment{#1}{}{}\renewenvironment{#1}}%
\let\newedcommand\renewedcommand
\let\renewedenvironment\newedenvironment
\makeatother
\let\mathon=$
\let\mathoff=$
\ifx\AtBeginDocument\undefined \newcommand{\AtBeginDocument}[1]{}\fi
\newbox\sizebox
\setlength{\hoffset}{0pt}\setlength{\voffset}{0pt}
\addtolength{\textheight}{\footskip}\setlength{\footskip}{0pt}
\addtolength{\textheight}{\topmargin}\setlength{\topmargin}{0pt}
\addtolength{\textheight}{\headheight}\setlength{\headheight}{0pt}
\addtolength{\textheight}{\headsep}\setlength{\headsep}{0pt}
\setlength{\textwidth}{349pt}
\newwrite\lthtmlwrite
\makeatletter
\let\realnormalsize=\normalsize
\global\topskip=2sp
\def\preveqno{}\let\real@float=\@float \let\realend@float=\end@float
\def\@float{\let\@savefreelist\@freelist\real@float}
\def\liih@math{\ifmmode$\else\bad@math\fi}
\def\end@float{\realend@float\global\let\@freelist\@savefreelist}
\let\real@dbflt=\@dbflt \let\end@dblfloat=\end@float
\let\@largefloatcheck=\relax
\let\if@boxedmulticols=\iftrue
\def\@dbflt{\let\@savefreelist\@freelist\real@dbflt}
\def\adjustnormalsize{\def\normalsize{\mathsurround=0pt \realnormalsize
 \parindent=0pt\abovedisplayskip=0pt\belowdisplayskip=0pt}%
 \def\phantompar{\csname par\endcsname}\normalsize}%
\def\lthtmltypeout#1{{\let\protect\string \immediate\write\lthtmlwrite{#1}}}%
\newcommand\lthtmlhboxmathA{\adjustnormalsize\setbox\sizebox=\hbox\bgroup\kern.05em }%
\newcommand\lthtmlhboxmathB{\adjustnormalsize\setbox\sizebox=\hbox to\hsize\bgroup\hfill }%
\newcommand\lthtmlvboxmathA{\adjustnormalsize\setbox\sizebox=\vbox\bgroup %
 \let\ifinner=\iffalse \let\)\liih@math }%
\newcommand\lthtmlboxmathZ{\@next\next\@currlist{}{\def\next{\voidb@x}}%
 \expandafter\box\next\egroup}%
\newcommand\lthtmlmathtype[1]{\gdef\lthtmlmathenv{#1}}%
\newcommand\lthtmllogmath{\dimen0\ht\sizebox \advance\dimen0\dp\sizebox
  \ifdim\dimen0>.95\vsize
   \lthtmltypeout{%
*** image for \lthtmlmathenv\space is too tall at \the\dimen0, reducing to .95 vsize ***}%
   \ht\sizebox.95\vsize \dp\sizebox\z@ \fi
  \lthtmltypeout{l2hSize %
:\lthtmlmathenv:\the\ht\sizebox::\the\dp\sizebox::\the\wd\sizebox.\preveqno}}%
\newcommand\lthtmlfigureA[1]{\let\@savefreelist\@freelist
       \lthtmlmathtype{#1}\lthtmlvboxmathA}%
\newcommand\lthtmlpictureA{\bgroup\catcode`\_=8 \lthtmlpictureB}%
\newcommand\lthtmlpictureB[1]{\lthtmlmathtype{#1}\egroup
       \let\@savefreelist\@freelist \lthtmlhboxmathB}%
\newcommand\lthtmlpictureZ[1]{\hfill\lthtmlfigureZ}%
\newcommand\lthtmlfigureZ{\lthtmlboxmathZ\lthtmllogmath\copy\sizebox
       \global\let\@freelist\@savefreelist}%
\newcommand\lthtmldisplayA{\bgroup\catcode`\_=8 \lthtmldisplayAi}%
\newcommand\lthtmldisplayAi[1]{\lthtmlmathtype{#1}\egroup\lthtmlvboxmathA}%
\newcommand\lthtmldisplayB[1]{\edef\preveqno{(\theequation)}%
  \lthtmldisplayA{#1}\let\@eqnnum\relax}%
\newcommand\lthtmldisplayZ{\lthtmlboxmathZ\lthtmllogmath\lthtmlsetmath}%
\newcommand\lthtmlinlinemathA{\bgroup\catcode`\_=8 \lthtmlinlinemathB}
\newcommand\lthtmlinlinemathB[1]{\lthtmlmathtype{#1}\egroup\lthtmlhboxmathA
  \vrule height1.5ex width0pt }%
\newcommand\lthtmlinlineA{\bgroup\catcode`\_=8 \lthtmlinlineB}%
\newcommand\lthtmlinlineB[1]{\lthtmlmathtype{#1}\egroup\lthtmlhboxmathA}%
\newcommand\lthtmlinlineZ{\egroup\expandafter\ifdim\dp\sizebox>0pt %
  \expandafter\centerinlinemath\fi\lthtmllogmath\lthtmlsetinline}
\newcommand\lthtmlinlinemathZ{\egroup\expandafter\ifdim\dp\sizebox>0pt %
  \expandafter\centerinlinemath\fi\lthtmllogmath\lthtmlsetmath}
\newcommand\lthtmlindisplaymathZ{\egroup %
  \centerinlinemath\lthtmllogmath\lthtmlsetmath}
\def\lthtmlsetinline{\hbox{\vrule width.1em \vtop{\vbox{%
  \kern.1em\copy\sizebox}\ifdim\dp\sizebox>0pt\kern.1em\else\kern.3pt\fi
  \ifdim\hsize>\wd\sizebox \hrule depth1pt\fi}}}
\def\lthtmlsetmath{\hbox{\vrule width.1em\kern-.05em\vtop{\vbox{%
  \kern.1em\kern0.8 pt\hbox{\hglue.17em\copy\sizebox\hglue0.8 pt}}\kern.3pt%
  \ifdim\dp\sizebox>0pt\kern.1em\fi \kern0.8 pt%
  \ifdim\hsize>\wd\sizebox \hrule depth1pt\fi}}}
\def\centerinlinemath{%
  \dimen1=\ifdim\ht\sizebox<\dp\sizebox \dp\sizebox\else\ht\sizebox\fi
  \advance\dimen1by.5pt \vrule width0pt height\dimen1 depth\dimen1 
 \dp\sizebox=\dimen1\ht\sizebox=\dimen1\relax}

\def\lthtmlcheckvsize{\ifdim\ht\sizebox<\vsize 
  \ifdim\wd\sizebox<\hsize\expandafter\hfill\fi \expandafter\vfill
  \else\expandafter\vss\fi}%
\providecommand{\selectlanguage}[1]{}%
\makeatletter \tracingstats = 1

\begin{document}
\pagestyle{empty}\thispagestyle{empty}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength hsize=\the\hsize}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength vsize=\the\vsize}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength hoffset=\the\hoffset}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength voffset=\the\voffset}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength topmargin=\the\topmargin}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength topskip=\the\topskip}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength headheight=\the\headheight}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength headsep=\the\headsep}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength parskip=\the\parskip}\lthtmltypeout{}%
\lthtmltypeout{latex2htmlLength oddsidemargin=\the\oddsidemargin}\lthtmltypeout{}%
\makeatletter
\if@twoside\lthtmltypeout{latex2htmlLength evensidemargin=\the\evensidemargin}%
\else\lthtmltypeout{latex2htmlLength evensidemargin=\the\oddsidemargin}\fi%
\lthtmltypeout{}%
\makeatother
\setcounter{page}{1}
\onecolumn

% !!! IMAGES START HERE !!!

{\newpage\clearpage
\lthtmlfigureA{cventries49}%
\begin{cventries}
\par
\cventry
  {PhD} % Degree
  {POSTECH, Graduate Institute of Ferrous Technology} % Institution
  {Pohang, Republic of Korea} % Location
  {Mar. 2010 - Feb. 2014} % Date(s)
  {
  }
\par
\cventry
  {MS} % Degree
  {POSTECH, Graduate Institute of Ferrous Technology} % Institution
  {Pohang, Republic of Korea} % Location
  {Mar. 2008 - Feb. 2010} % Date(s)
  {
  }
\par
\cventry
  {BS} % Degree
  {Hanyang University, Materials Science and Engineering} % Institution
  {Seoul, Republic of Korea} % Location
  {Mar. 2001 - Feb. 2008} % Date(s)
  {
  }
  % {
  \par
\end{cventries}%
\lthtmlfigureZ
\lthtmlcheckvsize\clearpage}

{\newpage\clearpage
\lthtmlfigureA{cventries77}%
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {Assistant professor} % Job title
  {Changwon National University}
  {Changwon, Republic of Korea} % Location
  {Mar. 2017, - present} % Date(s)
  {
  }
\par
\cventry
  {Post Doctorate Researcher} % Job title
  {POSTECH}
  {Pohang, Republic of Korea} % Location
  {Dec. 2016, - Feb. 2017} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Crystal plasticity modeling and simulations to predict bauschinger effects}
    \end{cvitems}
  }
\par
\cventry
  {Research Scientist} % Job title
  {Clemson University}
  {Greenville, SC, USA} % Location
  {Mar. 2016, - Nov. 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Formability predictions using VPSC-FLD}
    \item {Abaqus UMAT development}
    \end{cvitems}
  }
\par
\cventry
  {Post Doctorate Researcher} % Job title
  {National Institute of Standards and Technology} % Organization
  {Gaithersburg, MD, USA} % Location
  {Jan. 2014, - Feb. 2016} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Conducted a series of experiments to obtain multiaxial constitutive behavior of an interstitial-free steel}
    \item {Measured multiaxial flow stress using X-ray diffraction for metal sheets subjected to various multiaxial loading conditions (DiffStress package)}
    \item {Performed the strain analysis using digital image correlation technique to determine the forming limit diagram of the IF steel}
    \item {Developed the VPSC-FLD model to predict forming limit diagram of engineering metal sheets (VPSC-FLD package)}
    \item {Developed VPSC-based model to link with continuum-scale phenomenological model (VPSC-RGVB-YLD forked from VPSC-FLD)}
    \end{cvitems}
    % \begin{cvsubentries}
    }
\par
\cventry
  {Research Affiliate} % Job title
  {Los Alamos National Laboratory} % Organization
  {Los Alamos, NM, USA} % Location
  {Apr. 2012, - Sep. 2012} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      {Leading role in implementing a phase transformation kinetics model into Elasto-ViscoPlastic Self-Consistent crystal plasticity model}
    \end{cvitems}
  }
\par
\cventry
  {Guest Researcher} % Job title
  {National Institute of Standards and Technology} % Organization
  {Gaithersburg, MD, USA} % Location
  {June. 2011, - Dec. 2011} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      {Conducted experiments to obtain multiaxial stress-strain measurements using digital image correlation and in-situ X-ray technique}
    \end{cvitems}
  }
\par
\end{cventries}%
\lthtmlfigureZ
\lthtmlcheckvsize\clearpage}

{\newpage\clearpage
\lthtmlfigureA{cvskills144}%
\begin{cvskills}
  \cvskill
  {Programming}
  {Python, Fortran, Bash script, C/C++, LaTeX, Matlab}
\par
\cvskill
  {Languages}
  {Korean, English}
\par
\cvskill
  {Experimental Mechanics}
  {Uniaxial tension, shear, hydraulic bulge test, biaxial tests using cruciform piece and Marciniak}
\par
\cvskill
  {Digital Image Correlation (DIC)}
  {VIC3D}
\par
\cvskill
  {Diffraction experiments}
  {Pole figure, crystallographic texture, phase fraction, residual stress measurements}
\par
\cvskill
  {Computer skills}
  {Linux, Git, Abaqus (UMAT and Python script), Parallel computation}
\par
\cvskill
  {Constutitive modelling}
  {Macro-mechanical description for anisotropic metals using anisotropic yield functions}
\par
\cvskill
  {Crystal plasticity}
  {Viscoplastic self-consistent (VPSC) and Elasto-viscoplastic self-consistent crystal plasticity models}
\par
\end{cvskills}%
\lthtmlfigureZ
\lthtmlcheckvsize\clearpage}

{\newpage\clearpage
\lthtmlfigureA{cventries181}%
\begin{cventries}
  % ---------------------------------------------------------
  \cventry
  {\underline{Y. Jeong}$^*$, F. Barlat, C. Tom\'{e}, W. Wen}
  {\href{http://dx.doi.org/10.1016/j.ijplas.2016.07.015}{A comparative study between micro- and macro-mechanical constitutive models developed for complex loading scenarios}}
  {International Journal of Plasticity}
  {Vol. 93 p212-228, 2017} % etcs
  {
  }
\par
\cventry
  {\underline{Y. Jeong}$^*$, T. Gn\"{a}upel-Herold, M. Iadicola, A. Creuziger} % Authors
  {\href{https://doi.org/10.1107/S1600576716013662}{Uncertainty in flow stress measurements using X-ray diffraction for sheet metals subjected to large plastic deformations}} % Title
  {Journal of Applied Crystallography} % Journals
  {Vol. 49 p1991-2004, 2016} % etcs
  {
  }
\par
\cventry
  {D. Steglich, \underline{Y. Jeong}$^*$}
  {\href{http://dx.doi.org/10.1016/j.ijmecsci.2016.08.013}{Texture-based forming limit prediction for Mg sheet alloys ZE10 and AZ31}}
  { International Journal of Mechanical Sciences} % Journals
  {Vol. 117 p102-114, 2016} % etcs
  {
  }
\par
\cventry
  {\underline{Y. Jeong}$^*$, M.-S. Pham, M. Iadicola, A. Creuziger, T. Foecke}
  {\href{http://dx.doi.org/10.1088/0965-0393/24/5/055005}{Forming limit prediction using a self-consistent crystal plasticity framework: a case study for BCC fiber textures}}
  {Modelling and Simulation in Materials Science and Engineering}
  {Vol. 24(5), 055002 (21 pp), 2016} % etcs
  {
  }
\par
\cventry
  {\underline{Y. Jeong}$^*$, M. Iadicola, T. Gn\"{a}upel-Herold, A. Creuziger}
  {\href{http://dx.doi.org/10.1016/j.actamat.2016.04.013}{Multiaxial constitutive behavior of an interstitial-free steel: measurements through X-ray and digital image correlation}}
  {Acta Materialia }
  {Vol. 112 p84-93, 2016}
  {
  }
\par
\cventry
  {H. Wang$^*$, \underline{Y. Jeong}, B. Clausen, Y. Liu, R. J. McCabe, F. Barlat, C. N. Tom\'{e}}
  {\href{http://dx.doi.org/10.1016/j.msea.2015.09.108}{Effect of martensitic phase transformation on the behavior of 304 austenitic stainless steel under tension}}
  {Materials Science and Engineering A }
  {Vol. 649 p174-183, 2016}
  {
  }
\par
\cventry
  {\underline{Y. Jeong}, T. Gn\"{a}upel-Herold, F. Barlat, M. Iadicola, A. Creuziger, M.-G. Lee$^*$}
  {\href{http://dx.doi.org/10.1016/j.ijplas.2014.06.009}{Evaluation of biaxial flow stress based on Elasto-Viscoplastic Self-Consistent analysis of X-ray Diffraction Measurements}}
  {International Journal of Plasticity}
  {Vol. 66 p103-118, 2015}
  {
  }
\par
\cventry
  {\underline{Y. Jeong}$^*$, F. Barlat, M.-G. Lee}
  {\href{http://dx.doi.org/10.1088/0965-0393/20/2/024009}{Application of crystal plasticity to an austenitic stainless steel}}
  {Modelling and Simulation in Materials Science and Engineering}
  {Vol. 20 p024009, 2012}
  {
  }
\par
\cventry
  {D. Steglich$^*$, \underline{Y. Jeong}, M. O. Andar, T. Kuwabara}
  {\href{http://dx.doi.org/10.1016/j.ijsolstr.2012.06.017}{Biaxial Deformation Behavior of AZ31 Magnesium Alloy: Crystal-Plasticity-Based Prediction and Experimental Validation}}
  {International Journal of Solids and Structure}
  {Vol. 49(25) p3551-3561, 2012}
  {
  }
\item
\par
\end{cventries}%
\lthtmlfigureZ
\lthtmlcheckvsize\clearpage}

{\newpage\clearpage
\lthtmlfigureA{cventries243}%
\begin{cventries}
  % ---------------------------------------------------------
\item
  \cventry
  {F. Barlat, \underline{Y. Jeong}, J. Ha, C Tom\'{e}, Myoung-Gyu Lee, W. Wen}
  {\href{https://dx.doi.org/10.4028/www.scientific.net/KEM.725.3}{Advances in Constitutive Modeling of Plasticity for Forming Applications}}
  {Key Engineering Materials}
  {Vol. 725, p3-14, 2017}
  {
  }
\par
\cventry
  {\underline{Y. Jeong}, F. Barlat, C. Tom\'{e}, W. Wen}
  {\href{http://dx.doi.org/10.1063/1.4963544}{Validation of Homogeneous Anisotropic Hardening Approach Based on Crystal Plasticity}}
  {AIP Conference Proceedings}
  {Vol. 1769, 160001, 2016}
  {
  }
\par
\cventry
  {\underline{Y. Jeong}, M.-S. Pham, M. Iadicola, A. Creuziger}
  {\href{https://doi.org/10.4028/www.scientific.net/KEM.651-653.193}{Forming limit predictions using a self-consistent crystal plasticity model: a parametric study}}
  {Key Engineering Materials}
  {Vol. 651 p193-198, 2015  }
  {
  }
\par
\cventry
  {\underline{Y. Jeong}, F. Barlat, M.-G. Lee}
  {\href{https://doi.org/10.4028/www.scientific.net/MSF.702-703.224}{Microstructural and crystallographic aspects of yield surface evolution}}
  {Materials Science Forum}
  {Vol. 702 p224-228, 2011}
  {
  }
\par
\cventry
  {\underline{Y. Jeong}, F. Barlat, M.-G. Lee}
  {\href{https://doi.org/10.4028/www.scientific.net/MSF.702-703.204}{Crystal Plasticity Predictions of Forward-Reverse Simple Shear Flow Stress}}
  {Materials Science Forum}
  {Vol. 702 p204-207, 2011}
  {
  }
\item
\par
\end{cventries}%
\lthtmlfigureZ
\lthtmlcheckvsize\clearpage}

\end{document}

### 2018-05-24 mycv/subs/fundings.tex
tex files were added

\cvsection{Fundings}
\begin{cvhonors}

  \cvhonor
  {Multi-scale crystal plasticity framework for multiphase metals under non-linear forming scenario} %Award
  {NRF-2017R1D1A1B03031052}%EVENT
  {National Science Foundation of Korea} %Location
  {2017-2020} %dates

\end{cvhonors}

### 2018-05-24 mycv/subs/papers.tex
tex files were added

--- 2018-05-24 mycv/cv/images.tex
@@
-\batchmode
+%-------------------------------------------------------------------------------
+%	SECTION TITLE
+%-------------------------------------------------------------------------------
+\cvsection{Journal Articles}
 
-\documentclass[11pt,a4paper]{awesome-cv}
-
-\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
-
-\fontdir[fonts/]
-
-\colorlet{awesome}{awesome-red}
-
-\setbool{acvSectionColorHighlight}{true}
-
-%
-\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}
-
-\name{Youngung}{Jeong}
-\position{Assistant professor}
-\address{20 Changwondaehak-ro, Changwon, Gyeongnam, 51140, Republic of Korea}
-
-\mobile{(+82) 10-9763-3022}
-\email{yjeong@changwon.ac.kr}
-\homepage{52-208}
-\github{youngung}
-\gitlab{youngung.jeong}
-
-\usepackage[dvips]{color}
-
-\pagecolor[gray]{.7}
-
-\usepackage[]{inputenc}
-
-\makeatletter
-
-\makeatletter
-\count@=\the\catcode`\_ \catcode`\_=8 
-\newenvironment{tex2html_wrap}{}{}%
-\catcode`\<=12\catcode`\_=\count@
-\newcommand{\providedcommand}[1]{\expandafter\providecommand\csname #1\endcsname}%
-\newcommand{\renewedcommand}[1]{\expandafter\providecommand\csname #1\endcsname{}%
-  \expandafter\renewcommand\csname #1\endcsname}%
-\newcommand{\newedenvironment}[1]{\newenvironment{#1}{}{}\renewenvironment{#1}}%
-\let\newedcommand\renewedcommand
-\let\renewedenvironment\newedenvironment
-\makeatother
-\let\mathon=$
-\let\mathoff=$
-\ifx\AtBeginDocument\undefined \newcommand{\AtBeginDocument}[1]{}\fi
-\newbox\sizebox
-\setlength{\hoffset}{0pt}\setlength{\voffset}{0pt}
-\addtolength{\textheight}{\footskip}\setlength{\footskip}{0pt}
-\addtolength{\textheight}{\topmargin}\setlength{\topmargin}{0pt}
-\addtolength{\textheight}{\headheight}\setlength{\headheight}{0pt}
-\addtolength{\textheight}{\headsep}\setlength{\headsep}{0pt}
-\setlength{\textwidth}{349pt}
-\newwrite\lthtmlwrite
-\makeatletter
-\let\realnormalsize=\normalsize
-\global\topskip=2sp
-\def\preveqno{}\let\real@float=\@float \let\realend@float=\end@float
-\def\@float{\let\@savefreelist\@freelist\real@float}
-\def\liih@math{\ifmmode$\else\bad@math\fi}
-\def\end@float{\realend@float\global\let\@freelist\@savefreelist}
-\let\real@dbflt=\@dbflt \let\end@dblfloat=\end@float
-\let\@largefloatcheck=\relax
-\let\if@boxedmulticols=\iftrue
-\def\@dbflt{\let\@savefreelist\@freelist\real@dbflt}
-\def\adjustnormalsize{\def\normalsize{\mathsurround=0pt \realnormalsize
- \parindent=0pt\abovedisplayskip=0pt\belowdisplayskip=0pt}%
- \def\phantompar{\csname par\endcsname}\normalsize}%
-\def\lthtmltypeout#1{{\let\protect\string \immediate\write\lthtmlwrite{#1}}}%
-\newcommand\lthtmlhboxmathA{\adjustnormalsize\setbox\sizebox=\hbox\bgroup\kern.05em }%
-\newcommand\lthtmlhboxmathB{\adjustnormalsize\setbox\sizebox=\hbox to\hsize\bgroup\hfill }%
-\newcommand\lthtmlvboxmathA{\adjustnormalsize\setbox\sizebox=\vbox\bgroup %
- \let\ifinner=\iffalse \let\)\liih@math }%
-\newcommand\lthtmlboxmathZ{\@next\next\@currlist{}{\def\next{\voidb@x}}%
- \expandafter\box\next\egroup}%
-\newcommand\lthtmlmathtype[1]{\gdef\lthtmlmathenv{#1}}%
-\newcommand\lthtmllogmath{\dimen0\ht\sizebox \advance\dimen0\dp\sizebox
-  \ifdim\dimen0>.95\vsize
-   \lthtmltypeout{%
-*** image for \lthtmlmathenv\space is too tall at \the\dimen0, reducing to .95 vsize ***}%
-   \ht\sizebox.95\vsize \dp\sizebox\z@ \fi
-  \lthtmltypeout{l2hSize %
-:\lthtmlmathenv:\the\ht\sizebox::\the\dp\sizebox::\the\wd\sizebox.\preveqno}}%
-\newcommand\lthtmlfigureA[1]{\let\@savefreelist\@freelist
-       \lthtmlmathtype{#1}\lthtmlvboxmathA}%
-\newcommand\lthtmlpictureA{\bgroup\catcode`\_=8 \lthtmlpictureB}%
-\newcommand\lthtmlpictureB[1]{\lthtmlmathtype{#1}\egroup
-       \let\@savefreelist\@freelist \lthtmlhboxmathB}%
-\newcommand\lthtmlpictureZ[1]{\hfill\lthtmlfigureZ}%
-\newcommand\lthtmlfigureZ{\lthtmlboxmathZ\lthtmllogmath\copy\sizebox
-       \global\let\@freelist\@savefreelist}%
-\newcommand\lthtmldisplayA{\bgroup\catcode`\_=8 \lthtmldisplayAi}%
-\newcommand\lthtmldisplayAi[1]{\lthtmlmathtype{#1}\egroup\lthtmlvboxmathA}%
-\newcommand\lthtmldisplayB[1]{\edef\preveqno{(\theequation)}%
-  \lthtmldisplayA{#1}\let\@eqnnum\relax}%
-\newcommand\lthtmldisplayZ{\lthtmlboxmathZ\lthtmllogmath\lthtmlsetmath}%
-\newcommand\lthtmlinlinemathA{\bgroup\catcode`\_=8 \lthtmlinlinemathB}
-\newcommand\lthtmlinlinemathB[1]{\lthtmlmathtype{#1}\egroup\lthtmlhboxmathA
-  \vrule height1.5ex width0pt }%
-\newcommand\lthtmlinlineA{\bgroup\catcode`\_=8 \lthtmlinlineB}%
-\newcommand\lthtmlinlineB[1]{\lthtmlmathtype{#1}\egroup\lthtmlhboxmathA}%
-\newcommand\lthtmlinlineZ{\egroup\expandafter\ifdim\dp\sizebox>0pt %
-  \expandafter\centerinlinemath\fi\lthtmllogmath\lthtmlsetinline}
-\newcommand\lthtmlinlinemathZ{\egroup\expandafter\ifdim\dp\sizebox>0pt %
-  \expandafter\centerinlinemath\fi\lthtmllogmath\lthtmlsetmath}
-\newcommand\lthtmlindisplaymathZ{\egroup %
-  \centerinlinemath\lthtmllogmath\lthtmlsetmath}
-\def\lthtmlsetinline{\hbox{\vrule width.1em \vtop{\vbox{%
-  \kern.1em\copy\sizebox}\ifdim\dp\sizebox>0pt\kern.1em\else\kern.3pt\fi
-  \ifdim\hsize>\wd\sizebox \hrule depth1pt\fi}}}
-\def\lthtmlsetmath{\hbox{\vrule width.1em\kern-.05em\vtop{\vbox{%
-  \kern.1em\kern0.8 pt\hbox{\hglue.17em\copy\sizebox\hglue0.8 pt}}\kern.3pt%
-  \ifdim\dp\sizebox>0pt\kern.1em\fi \kern0.8 pt%
-  \ifdim\hsize>\wd\sizebox \hrule depth1pt\fi}}}
-\def\centerinlinemath{%
-  \dimen1=\ifdim\ht\sizebox<\dp\sizebox \dp\sizebox\else\ht\sizebox\fi
-  \advance\dimen1by.5pt \vrule width0pt height\dimen1 depth\dimen1 
- \dp\sizebox=\dimen1\ht\sizebox=\dimen1\relax}
-
-\def\lthtmlcheckvsize{\ifdim\ht\sizebox<\vsize 
-  \ifdim\wd\sizebox<\hsize\expandafter\hfill\fi \expandafter\vfill
-  \else\expandafter\vss\fi}%
-\providecommand{\selectlanguage}[1]{}%
-\makeatletter \tracingstats = 1
-
-\begin{document}
-\pagestyle{empty}\thispagestyle{empty}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength hsize=\the\hsize}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength vsize=\the\vsize}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength hoffset=\the\hoffset}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength voffset=\the\voffset}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength topmargin=\the\topmargin}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength topskip=\the\topskip}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength headheight=\the\headheight}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength headsep=\the\headsep}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength parskip=\the\parskip}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength oddsidemargin=\the\oddsidemargin}\lthtmltypeout{}%
-\makeatletter
-\if@twoside\lthtmltypeout{latex2htmlLength evensidemargin=\the\evensidemargin}%
-\else\lthtmltypeout{latex2htmlLength evensidemargin=\the\oddsidemargin}\fi%
-\lthtmltypeout{}%
-\makeatother
-\setcounter{page}{1}
-\onecolumn
-
-% !!! IMAGES START HERE !!!
-
-{\newpage\clearpage
-\lthtmlfigureA{cventries49}%
-\begin{cventries}
-\par
-\cventry
-  {PhD} % Degree
-  {POSTECH, Graduate Institute of Ferrous Technology} % Institution
-  {Pohang, Republic of Korea} % Location
-  {Mar. 2010 - Feb. 2014} % Date(s)
-  {
-  }
-\par
-\cventry
-  {MS} % Degree
-  {POSTECH, Graduate Institute of Ferrous Technology} % Institution
-  {Pohang, Republic of Korea} % Location
-  {Mar. 2008 - Feb. 2010} % Date(s)
-  {
-  }
-\par
-\cventry
-  {BS} % Degree
-  {Hanyang University, Materials Science and Engineering} % Institution
-  {Seoul, Republic of Korea} % Location
-  {Mar. 2001 - Feb. 2008} % Date(s)
-  {
-  }
-  % {
-  \par
-\end{cventries}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
-
-{\newpage\clearpage
-\lthtmlfigureA{cventries77}%
+%-------------------------------------------------------------------------------
+%	CONTENT
+%-------------------------------------------------------------------------------
 \begin{cventries}
@@
   \cventry
-  {Assistant professor} % Job title
-  {Changwon National University}
-  {Changwon, Republic of Korea} % Location
-  {Mar. 2017, - present} % Date(s)
+  {H. Kim, F Barlat, Y. Lee, S. Zaman, CS Lee, \underline{Y. Jeong}$^*$}
+  {A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}
+  {Submitted}
+  {}
+%  {International Journal of Plasticity}
+%  {Vol. 93 p212-228, 2017} % etcs
   {
   }
-\par
-\cventry
-  {Post Doctorate Researcher} % Job title
-  {POSTECH}
-  {Pohang, Republic of Korea} % Location
-  {Dec. 2016, - Feb. 2017} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-    \item {Crystal plasticity modeling and simulations to predict bauschinger effects}
-    \end{cvitems}
-  }
-\par
-\cventry
-  {Research Scientist} % Job title
-  {Clemson University}
-  {Greenville, SC, USA} % Location
-  {Mar. 2016, - Nov. 2016} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-    \item {Formability predictions using VPSC-FLD}
-    \item {Abaqus UMAT development}
-    \end{cvitems}
-  }
-\par
-\cventry
-  {Post Doctorate Researcher} % Job title
-  {National Institute of Standards and Technology} % Organization
-  {Gaithersburg, MD, USA} % Location
-  {Jan. 2014, - Feb. 2016} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-    \item {Conducted a series of experiments to obtain multiaxial constitutive behavior of an interstitial-free steel}
-    \item {Measured multiaxial flow stress using X-ray diffraction for metal sheets subjected to various multiaxial loading conditions (DiffStress package)}
-    \item {Performed the strain analysis using digital image correlation technique to determine the forming limit diagram of the IF steel}
-    \item {Developed the VPSC-FLD model to predict forming limit diagram of engineering metal sheets (VPSC-FLD package)}
-    \item {Developed VPSC-based model to link with continuum-scale phenomenological model (VPSC-RGVB-YLD forked from VPSC-FLD)}
-    \end{cvitems}
-    % \begin{cvsubentries}
-    }
-\par
-\cventry
-  {Research Affiliate} % Job title
-  {Los Alamos National Laboratory} % Organization
-  {Los Alamos, NM, USA} % Location
-  {Apr. 2012, - Sep. 2012} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-      {Leading role in implementing a phase transformation kinetics model into Elasto-ViscoPlastic Self-Consistent crystal plasticity model}
-    \end{cvitems}
-  }
-\par
-\cventry
-  {Guest Researcher} % Job title
-  {National Institute of Standards and Technology} % Organization
-  {Gaithersburg, MD, USA} % Location
-  {June. 2011, - Dec. 2011} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-      {Conducted experiments to obtain multiaxial stress-strain measurements using digital image correlation and in-situ X-ray technique}
-    \end{cvitems}
-  }
-\par
-\end{cventries}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
 
-{\newpage\clearpage
-\lthtmlfigureA{cvskills144}%
-\begin{cvskills}
-  \cvskill
-  {Programming}
-  {Python, Fortran, Bash script, C/C++, LaTeX, Matlab}
-\par
-\cvskill
-  {Languages}
-  {Korean, English}
-\par
-\cvskill
-  {Experimental Mechanics}
-  {Uniaxial tension, shear, hydraulic bulge test, biaxial tests using cruciform piece and Marciniak}
-\par
-\cvskill
-  {Digital Image Correlation (DIC)}
-  {VIC3D}
-\par
-\cvskill
-  {Diffraction experiments}
-  {Pole figure, crystallographic texture, phase fraction, residual stress measurements}
-\par
-\cvskill
-  {Computer skills}
-  {Linux, Git, Abaqus (UMAT and Python script), Parallel computation}
-\par
-\cvskill
-  {Constutitive modelling}
-  {Macro-mechanical description for anisotropic metals using anisotropic yield functions}
-\par
-\cvskill
-  {Crystal plasticity}
-  {Viscoplastic self-consistent (VPSC) and Elasto-viscoplastic self-consistent crystal plasticity models}
-\par
-\end{cvskills}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
-
-{\newpage\clearpage
-\lthtmlfigureA{cventries181}%
-\begin{cventries}
   % ---------------------------------------------------------
@@
   }
-\par
+
+  % ---------------------------------------------------------
   \cventry
@@
   {\href{http://dx.doi.org/10.1016/j.ijmecsci.2016.08.013}{Texture-based forming limit prediction for Mg sheet alloys ZE10 and AZ31}}
-  { International Journal of Mechanical Sciences} % Journals
+  {International Journal of Mechanical Sciences} % Journals
   {Vol. 117 p102-114, 2016} % etcs
@@
 \item
-\par
-\end{cventries}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
 
-{\newpage\clearpage
-\lthtmlfigureA{cventries243}%
+\end{cventries}
+
+%-------------------------------------------------------------------------------
+%	SECTION TITLE
+%-------------------------------------------------------------------------------
+\cvsection{Conference proceedings}
+
+%-------------------------------------------------------------------------------
+%	CONTENT
+%-------------------------------------------------------------------------------
 \begin{cventries}
@@
   }
-\par
+
   \cventry
@@
 \item
-\par
-\end{cventries}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
 
-\end{document}
+\end{cventries}

### 2018-05-24 mycv/subs/skills.tex
tex files were added

--- 2018-05-24 mycv/cv/images.tex
@@
-\batchmode
+%-------------------------------------------------------------------------------
+%	SECTION TITLE
+%-------------------------------------------------------------------------------
+\cvsection{Skills}
 
-\documentclass[11pt,a4paper]{awesome-cv}
-
-\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
-
-\fontdir[fonts/]
-
-\colorlet{awesome}{awesome-red}
-
-\setbool{acvSectionColorHighlight}{true}
-
-%
-\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}
-
-\name{Youngung}{Jeong}
-\position{Assistant professor}
-\address{20 Changwondaehak-ro, Changwon, Gyeongnam, 51140, Republic of Korea}
-
-\mobile{(+82) 10-9763-3022}
-\email{yjeong@changwon.ac.kr}
-\homepage{52-208}
-\github{youngung}
-\gitlab{youngung.jeong}
-
-\usepackage[dvips]{color}
-
-\pagecolor[gray]{.7}
-
-\usepackage[]{inputenc}
-
-\makeatletter
-
-\makeatletter
-\count@=\the\catcode`\_ \catcode`\_=8 
-\newenvironment{tex2html_wrap}{}{}%
-\catcode`\<=12\catcode`\_=\count@
-\newcommand{\providedcommand}[1]{\expandafter\providecommand\csname #1\endcsname}%
-\newcommand{\renewedcommand}[1]{\expandafter\providecommand\csname #1\endcsname{}%
-  \expandafter\renewcommand\csname #1\endcsname}%
-\newcommand{\newedenvironment}[1]{\newenvironment{#1}{}{}\renewenvironment{#1}}%
-\let\newedcommand\renewedcommand
-\let\renewedenvironment\newedenvironment
-\makeatother
-\let\mathon=$
-\let\mathoff=$
-\ifx\AtBeginDocument\undefined \newcommand{\AtBeginDocument}[1]{}\fi
-\newbox\sizebox
-\setlength{\hoffset}{0pt}\setlength{\voffset}{0pt}
-\addtolength{\textheight}{\footskip}\setlength{\footskip}{0pt}
-\addtolength{\textheight}{\topmargin}\setlength{\topmargin}{0pt}
-\addtolength{\textheight}{\headheight}\setlength{\headheight}{0pt}
-\addtolength{\textheight}{\headsep}\setlength{\headsep}{0pt}
-\setlength{\textwidth}{349pt}
-\newwrite\lthtmlwrite
-\makeatletter
-\let\realnormalsize=\normalsize
-\global\topskip=2sp
-\def\preveqno{}\let\real@float=\@float \let\realend@float=\end@float
-\def\@float{\let\@savefreelist\@freelist\real@float}
-\def\liih@math{\ifmmode$\else\bad@math\fi}
-\def\end@float{\realend@float\global\let\@freelist\@savefreelist}
-\let\real@dbflt=\@dbflt \let\end@dblfloat=\end@float
-\let\@largefloatcheck=\relax
-\let\if@boxedmulticols=\iftrue
-\def\@dbflt{\let\@savefreelist\@freelist\real@dbflt}
-\def\adjustnormalsize{\def\normalsize{\mathsurround=0pt \realnormalsize
- \parindent=0pt\abovedisplayskip=0pt\belowdisplayskip=0pt}%
- \def\phantompar{\csname par\endcsname}\normalsize}%
-\def\lthtmltypeout#1{{\let\protect\string \immediate\write\lthtmlwrite{#1}}}%
-\newcommand\lthtmlhboxmathA{\adjustnormalsize\setbox\sizebox=\hbox\bgroup\kern.05em }%
-\newcommand\lthtmlhboxmathB{\adjustnormalsize\setbox\sizebox=\hbox to\hsize\bgroup\hfill }%
-\newcommand\lthtmlvboxmathA{\adjustnormalsize\setbox\sizebox=\vbox\bgroup %
- \let\ifinner=\iffalse \let\)\liih@math }%
-\newcommand\lthtmlboxmathZ{\@next\next\@currlist{}{\def\next{\voidb@x}}%
- \expandafter\box\next\egroup}%
-\newcommand\lthtmlmathtype[1]{\gdef\lthtmlmathenv{#1}}%
-\newcommand\lthtmllogmath{\dimen0\ht\sizebox \advance\dimen0\dp\sizebox
-  \ifdim\dimen0>.95\vsize
-   \lthtmltypeout{%
-*** image for \lthtmlmathenv\space is too tall at \the\dimen0, reducing to .95 vsize ***}%
-   \ht\sizebox.95\vsize \dp\sizebox\z@ \fi
-  \lthtmltypeout{l2hSize %
-:\lthtmlmathenv:\the\ht\sizebox::\the\dp\sizebox::\the\wd\sizebox.\preveqno}}%
-\newcommand\lthtmlfigureA[1]{\let\@savefreelist\@freelist
-       \lthtmlmathtype{#1}\lthtmlvboxmathA}%
-\newcommand\lthtmlpictureA{\bgroup\catcode`\_=8 \lthtmlpictureB}%
-\newcommand\lthtmlpictureB[1]{\lthtmlmathtype{#1}\egroup
-       \let\@savefreelist\@freelist \lthtmlhboxmathB}%
-\newcommand\lthtmlpictureZ[1]{\hfill\lthtmlfigureZ}%
-\newcommand\lthtmlfigureZ{\lthtmlboxmathZ\lthtmllogmath\copy\sizebox
-       \global\let\@freelist\@savefreelist}%
-\newcommand\lthtmldisplayA{\bgroup\catcode`\_=8 \lthtmldisplayAi}%
-\newcommand\lthtmldisplayAi[1]{\lthtmlmathtype{#1}\egroup\lthtmlvboxmathA}%
-\newcommand\lthtmldisplayB[1]{\edef\preveqno{(\theequation)}%
-  \lthtmldisplayA{#1}\let\@eqnnum\relax}%
-\newcommand\lthtmldisplayZ{\lthtmlboxmathZ\lthtmllogmath\lthtmlsetmath}%
-\newcommand\lthtmlinlinemathA{\bgroup\catcode`\_=8 \lthtmlinlinemathB}
-\newcommand\lthtmlinlinemathB[1]{\lthtmlmathtype{#1}\egroup\lthtmlhboxmathA
-  \vrule height1.5ex width0pt }%
-\newcommand\lthtmlinlineA{\bgroup\catcode`\_=8 \lthtmlinlineB}%
-\newcommand\lthtmlinlineB[1]{\lthtmlmathtype{#1}\egroup\lthtmlhboxmathA}%
-\newcommand\lthtmlinlineZ{\egroup\expandafter\ifdim\dp\sizebox>0pt %
-  \expandafter\centerinlinemath\fi\lthtmllogmath\lthtmlsetinline}
-\newcommand\lthtmlinlinemathZ{\egroup\expandafter\ifdim\dp\sizebox>0pt %
-  \expandafter\centerinlinemath\fi\lthtmllogmath\lthtmlsetmath}
-\newcommand\lthtmlindisplaymathZ{\egroup %
-  \centerinlinemath\lthtmllogmath\lthtmlsetmath}
-\def\lthtmlsetinline{\hbox{\vrule width.1em \vtop{\vbox{%
-  \kern.1em\copy\sizebox}\ifdim\dp\sizebox>0pt\kern.1em\else\kern.3pt\fi
-  \ifdim\hsize>\wd\sizebox \hrule depth1pt\fi}}}
-\def\lthtmlsetmath{\hbox{\vrule width.1em\kern-.05em\vtop{\vbox{%
-  \kern.1em\kern0.8 pt\hbox{\hglue.17em\copy\sizebox\hglue0.8 pt}}\kern.3pt%
-  \ifdim\dp\sizebox>0pt\kern.1em\fi \kern0.8 pt%
-  \ifdim\hsize>\wd\sizebox \hrule depth1pt\fi}}}
-\def\centerinlinemath{%
-  \dimen1=\ifdim\ht\sizebox<\dp\sizebox \dp\sizebox\else\ht\sizebox\fi
-  \advance\dimen1by.5pt \vrule width0pt height\dimen1 depth\dimen1 
- \dp\sizebox=\dimen1\ht\sizebox=\dimen1\relax}
-
-\def\lthtmlcheckvsize{\ifdim\ht\sizebox<\vsize 
-  \ifdim\wd\sizebox<\hsize\expandafter\hfill\fi \expandafter\vfill
-  \else\expandafter\vss\fi}%
-\providecommand{\selectlanguage}[1]{}%
-\makeatletter \tracingstats = 1
-
-\begin{document}
-\pagestyle{empty}\thispagestyle{empty}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength hsize=\the\hsize}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength vsize=\the\vsize}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength hoffset=\the\hoffset}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength voffset=\the\voffset}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength topmargin=\the\topmargin}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength topskip=\the\topskip}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength headheight=\the\headheight}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength headsep=\the\headsep}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength parskip=\the\parskip}\lthtmltypeout{}%
-\lthtmltypeout{latex2htmlLength oddsidemargin=\the\oddsidemargin}\lthtmltypeout{}%
-\makeatletter
-\if@twoside\lthtmltypeout{latex2htmlLength evensidemargin=\the\evensidemargin}%
-\else\lthtmltypeout{latex2htmlLength evensidemargin=\the\oddsidemargin}\fi%
-\lthtmltypeout{}%
-\makeatother
-\setcounter{page}{1}
-\onecolumn
-
-% !!! IMAGES START HERE !!!
-
-{\newpage\clearpage
-\lthtmlfigureA{cventries49}%
-\begin{cventries}
-\par
-\cventry
-  {PhD} % Degree
-  {POSTECH, Graduate Institute of Ferrous Technology} % Institution
-  {Pohang, Republic of Korea} % Location
-  {Mar. 2010 - Feb. 2014} % Date(s)
-  {
-  }
-\par
-\cventry
-  {MS} % Degree
-  {POSTECH, Graduate Institute of Ferrous Technology} % Institution
-  {Pohang, Republic of Korea} % Location
-  {Mar. 2008 - Feb. 2010} % Date(s)
-  {
-  }
-\par
-\cventry
-  {BS} % Degree
-  {Hanyang University, Materials Science and Engineering} % Institution
-  {Seoul, Republic of Korea} % Location
-  {Mar. 2001 - Feb. 2008} % Date(s)
-  {
-  }
-  % {
-  \par
-\end{cventries}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
-
-{\newpage\clearpage
-\lthtmlfigureA{cventries77}%
-\begin{cventries}
-  % ---------------------------------------------------------
-  \cventry
-  {Assistant professor} % Job title
-  {Changwon National University}
-  {Changwon, Republic of Korea} % Location
-  {Mar. 2017, - present} % Date(s)
-  {
-  }
-\par
-\cventry
-  {Post Doctorate Researcher} % Job title
-  {POSTECH}
-  {Pohang, Republic of Korea} % Location
-  {Dec. 2016, - Feb. 2017} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-    \item {Crystal plasticity modeling and simulations to predict bauschinger effects}
-    \end{cvitems}
-  }
-\par
-\cventry
-  {Research Scientist} % Job title
-  {Clemson University}
-  {Greenville, SC, USA} % Location
-  {Mar. 2016, - Nov. 2016} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-    \item {Formability predictions using VPSC-FLD}
-    \item {Abaqus UMAT development}
-    \end{cvitems}
-  }
-\par
-\cventry
-  {Post Doctorate Researcher} % Job title
-  {National Institute of Standards and Technology} % Organization
-  {Gaithersburg, MD, USA} % Location
-  {Jan. 2014, - Feb. 2016} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-    \item {Conducted a series of experiments to obtain multiaxial constitutive behavior of an interstitial-free steel}
-    \item {Measured multiaxial flow stress using X-ray diffraction for metal sheets subjected to various multiaxial loading conditions (DiffStress package)}
-    \item {Performed the strain analysis using digital image correlation technique to determine the forming limit diagram of the IF steel}
-    \item {Developed the VPSC-FLD model to predict forming limit diagram of engineering metal sheets (VPSC-FLD package)}
-    \item {Developed VPSC-based model to link with continuum-scale phenomenological model (VPSC-RGVB-YLD forked from VPSC-FLD)}
-    \end{cvitems}
-    % \begin{cvsubentries}
-    }
-\par
-\cventry
-  {Research Affiliate} % Job title
-  {Los Alamos National Laboratory} % Organization
-  {Los Alamos, NM, USA} % Location
-  {Apr. 2012, - Sep. 2012} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-      {Leading role in implementing a phase transformation kinetics model into Elasto-ViscoPlastic Self-Consistent crystal plasticity model}
-    \end{cvitems}
-  }
-\par
-\cventry
-  {Guest Researcher} % Job title
-  {National Institute of Standards and Technology} % Organization
-  {Gaithersburg, MD, USA} % Location
-  {June. 2011, - Dec. 2011} % Date(s)
-  {
-    \begin{cvitems} % Description(s) of tasks/responsibilities
-      {Conducted experiments to obtain multiaxial stress-strain measurements using digital image correlation and in-situ X-ray technique}
-    \end{cvitems}
-  }
-\par
-\end{cventries}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
-
-{\newpage\clearpage
-\lthtmlfigureA{cvskills144}%
+%-------------------------------------------------------------------------------
+%	CONTENT
+%-------------------------------------------------------------------------------
 \begin{cvskills}
@@
   {Python, Fortran, Bash script, C/C++, LaTeX, Matlab}
-\par
+
   \cvskill
@@
   {Korean, English}
-\par
+
   \cvskill
@@
   {Uniaxial tension, shear, hydraulic bulge test, biaxial tests using cruciform piece and Marciniak}
-\par
+
   \cvskill
@@
   {VIC3D}
-\par
+
   \cvskill
@@
   {Pole figure, crystallographic texture, phase fraction, residual stress measurements}
-\par
+
   \cvskill
@@
   {Linux, Git, Abaqus (UMAT and Python script), Parallel computation}
-\par
+
   \cvskill
@@
   {Macro-mechanical description for anisotropic metals using anisotropic yield functions}
-\par
+
   \cvskill
@@
   {Viscoplastic self-consistent (VPSC) and Elasto-viscoplastic self-consistent crystal plasticity models}
-\par
-\end{cvskills}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
 
-{\newpage\clearpage
-\lthtmlfigureA{cventries181}%
-\begin{cventries}
-  % ---------------------------------------------------------
-  \cventry
-  {\underline{Y. Jeong}$^*$, F. Barlat, C. Tom\'{e}, W. Wen}
-  {\href{http://dx.doi.org/10.1016/j.ijplas.2016.07.015}{A comparative study between micro- and macro-mechanical constitutive models developed for complex loading scenarios}}
-  {International Journal of Plasticity}
-  {Vol. 93 p212-228, 2017} % etcs
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}$^*$, T. Gn\"{a}upel-Herold, M. Iadicola, A. Creuziger} % Authors
-  {\href{https://doi.org/10.1107/S1600576716013662}{Uncertainty in flow stress measurements using X-ray diffraction for sheet metals subjected to large plastic deformations}} % Title
-  {Journal of Applied Crystallography} % Journals
-  {Vol. 49 p1991-2004, 2016} % etcs
-  {
-  }
-\par
-\cventry
-  {D. Steglich, \underline{Y. Jeong}$^*$}
-  {\href{http://dx.doi.org/10.1016/j.ijmecsci.2016.08.013}{Texture-based forming limit prediction for Mg sheet alloys ZE10 and AZ31}}
-  { International Journal of Mechanical Sciences} % Journals
-  {Vol. 117 p102-114, 2016} % etcs
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}$^*$, M.-S. Pham, M. Iadicola, A. Creuziger, T. Foecke}
-  {\href{http://dx.doi.org/10.1088/0965-0393/24/5/055005}{Forming limit prediction using a self-consistent crystal plasticity framework: a case study for BCC fiber textures}}
-  {Modelling and Simulation in Materials Science and Engineering}
-  {Vol. 24(5), 055002 (21 pp), 2016} % etcs
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}$^*$, M. Iadicola, T. Gn\"{a}upel-Herold, A. Creuziger}
-  {\href{http://dx.doi.org/10.1016/j.actamat.2016.04.013}{Multiaxial constitutive behavior of an interstitial-free steel: measurements through X-ray and digital image correlation}}
-  {Acta Materialia }
-  {Vol. 112 p84-93, 2016}
-  {
-  }
-\par
-\cventry
-  {H. Wang$^*$, \underline{Y. Jeong}, B. Clausen, Y. Liu, R. J. McCabe, F. Barlat, C. N. Tom\'{e}}
-  {\href{http://dx.doi.org/10.1016/j.msea.2015.09.108}{Effect of martensitic phase transformation on the behavior of 304 austenitic stainless steel under tension}}
-  {Materials Science and Engineering A }
-  {Vol. 649 p174-183, 2016}
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}, T. Gn\"{a}upel-Herold, F. Barlat, M. Iadicola, A. Creuziger, M.-G. Lee$^*$}
-  {\href{http://dx.doi.org/10.1016/j.ijplas.2014.06.009}{Evaluation of biaxial flow stress based on Elasto-Viscoplastic Self-Consistent analysis of X-ray Diffraction Measurements}}
-  {International Journal of Plasticity}
-  {Vol. 66 p103-118, 2015}
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}$^*$, F. Barlat, M.-G. Lee}
-  {\href{http://dx.doi.org/10.1088/0965-0393/20/2/024009}{Application of crystal plasticity to an austenitic stainless steel}}
-  {Modelling and Simulation in Materials Science and Engineering}
-  {Vol. 20 p024009, 2012}
-  {
-  }
-\par
-\cventry
-  {D. Steglich$^*$, \underline{Y. Jeong}, M. O. Andar, T. Kuwabara}
-  {\href{http://dx.doi.org/10.1016/j.ijsolstr.2012.06.017}{Biaxial Deformation Behavior of AZ31 Magnesium Alloy: Crystal-Plasticity-Based Prediction and Experimental Validation}}
-  {International Journal of Solids and Structure}
-  {Vol. 49(25) p3551-3561, 2012}
-  {
-  }
-\item
-\par
-\end{cventries}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
-
-{\newpage\clearpage
-\lthtmlfigureA{cventries243}%
-\begin{cventries}
-  % ---------------------------------------------------------
-\item
-  \cventry
-  {F. Barlat, \underline{Y. Jeong}, J. Ha, C Tom\'{e}, Myoung-Gyu Lee, W. Wen}
-  {\href{https://dx.doi.org/10.4028/www.scientific.net/KEM.725.3}{Advances in Constitutive Modeling of Plasticity for Forming Applications}}
-  {Key Engineering Materials}
-  {Vol. 725, p3-14, 2017}
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}, F. Barlat, C. Tom\'{e}, W. Wen}
-  {\href{http://dx.doi.org/10.1063/1.4963544}{Validation of Homogeneous Anisotropic Hardening Approach Based on Crystal Plasticity}}
-  {AIP Conference Proceedings}
-  {Vol. 1769, 160001, 2016}
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}, M.-S. Pham, M. Iadicola, A. Creuziger}
-  {\href{https://doi.org/10.4028/www.scientific.net/KEM.651-653.193}{Forming limit predictions using a self-consistent crystal plasticity model: a parametric study}}
-  {Key Engineering Materials}
-  {Vol. 651 p193-198, 2015  }
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}, F. Barlat, M.-G. Lee}
-  {\href{https://doi.org/10.4028/www.scientific.net/MSF.702-703.224}{Microstructural and crystallographic aspects of yield surface evolution}}
-  {Materials Science Forum}
-  {Vol. 702 p224-228, 2011}
-  {
-  }
-\par
-\cventry
-  {\underline{Y. Jeong}, F. Barlat, M.-G. Lee}
-  {\href{https://doi.org/10.4028/www.scientific.net/MSF.702-703.204}{Crystal Plasticity Predictions of Forward-Reverse Simple Shear Flow Stress}}
-  {Materials Science Forum}
-  {Vol. 702 p204-207, 2011}
-  {
-  }
-\item
-\par
-\end{cventries}%
-\lthtmlfigureZ
-\lthtmlcheckvsize\clearpage}
-
-\end{document}
+\end{cvskills}

### 2018-08-03 mycv/subs/fundings.tex
updates

@@
   \cvhonor
+  {}
+  {}
+  {\href{http://www.motie.go.kr/www/main.do}{South Korean Ministry of Trade, Industry and Energy}}
+  {2018-2021}
+
+  \cvhonor
   {Multi-scale crystal plasticity framework for multiphase metals under non-linear forming scenario} %Award
   {NRF-2017R1D1A1B03031052}%EVENT
-  {National Science Foundation of Korea} %Location
+  {NSF of Korea} %Location
   {2017-2020} %dates

### 2018-08-03 mycv/subs/papers.tex
updates

@@
   {H. Kim, F Barlat, Y. Lee, S. Zaman, CS Lee, \underline{Y. Jeong}$^*$}
-  {A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}
-  {Submitted}
-  {}
-%  {International Journal of Plasticity}
-%  {Vol. 93 p212-228, 2017} % etcs
+  {\href{https://doi.org/10.1016/j.ijplas.2018.07.010}{A crystal plasticity model for describing the anisotropic hardening behavior of steel sheets during strain-path changes}}
+  {International Journal of Plasticity}
+  {In press}
   {

### 2018-08-27 mycv/subs/papers.tex
updates

@@
   \cventry
+  {\underline{Y. Jeong}, T. Manninen}
+  {\href{https://doi.org/10.1088/1742-6596/1063/1/012020}{Formability predictions and measurement of 316L stainless steel using self-consistent crystal plasticity}}
+  {Journal of Physics: Conference Series}
+  {Vol. 1063, 2018}
+  {
+  }
+
+  \cventry
+  {\underline{Y. Jeong}, S. Panich}
+  {\href{https://doi.org/10.1016/j.promfg.2018.07.209}{Forming limits of dual phase steels using crystal plasticity in conjunction with MK approach}}
+  {Procedia Manufacturing}
+  {Vol. 15, 1816-1824, 2018}
+  {
+  }
+
+  \cventry
+  {D. Steglich \underline{Y. Jeong}}
+  {\href{https://doi.org/10.1063/1.5007958}{Texture-based formability prediction for Mg wrought alloys ZE10 and AZ31}}
+  {AIP Conference Proceedings}
+  {Vol. 1896, 020001, 2017}
+  {
+  }
+
+  \cventry
   {F. Barlat, \underline{Y. Jeong}, J. Ha, C Tom\'{e}, Myoung-Gyu Lee, W. Wen}

### 2018-12-26 mycv/subs/papers.tex
Updates

@@
     % ---------------------------------------------------------
+  % ---------------------------------------------------------
   \cventry
@@
   {International Journal of Plasticity}
-  {In press}
+  {Vol. 111 p85-106, 2018}
   {
@@
     \cventry
-  {\underline{Y. Jeong}, T. Manninen}
-  {\href{https://doi.org/10.1088/1742-6596/1063/1/012020}{Formability predictions and measurement of 316L stainless steel using self-consistent crystal plasticity}}
+  {\underline{Y. Jeong}$^*$, Timo Manninen}
+  {\href{http://iopscience.iop.org/article/10.1088/1742-6596/1063/1/012020}{Formability predictions and measurement of 316L stainless steel using self-consistent crystal plasticity}}
   {Journal of Physics: Conference Series}
-  {Vol. 1063, 2018}
+  {Vol. 150673, 2018}
   {
@@
 
+  % ---------------------------------------------------------
   \cventry
-  {\underline{Y. Jeong}, S. Panich}
+  {\underline{Y. Jeong}$^*$, S. Panich}
   {\href{https://doi.org/10.1016/j.promfg.2018.07.209}{Forming limits of dual phase steels using crystal plasticity in conjunction with MK approach}}
   {Procedia Manufacturing}
-  {Vol. 15, 1816-1824, 2018}
+  {Vol. 15, 2018}
   {

### 2019-08-15 mycv/subs/papers.tex
Entries
Updates

@@
   % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
+  {Extension of the VPSC model to account for elasto-visco-plastic behavior using a perturbed viscoplastic approach}
+  {Submitted}
+  {}
+  {
+  }
+
+  % ---------------------------------------------------------
+  \cventry
+  {S. J. Park, \underline{Y. Jeong}, C. W. Kim, J. H. Lee, S. C. Cho, S. B. Lee, S. K. Lee, D. H. Kim, H. U. Hong$^*$}
+  {\href{https://doi.org/10.1016/j.msea.2019.138260}{Superior tensile fracture strength of hot isostatically pressed TiC–steel metallic composite fabricated by a novel infiltration}}
+  {Materials Science and Engineering: A}
+  {Vol. 764(9), 2019}
+  {
+  }
+
+  % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, Timo Manninen}
+  {\href{10.1007/s12540-019-00292-5}{Enhancement in viscoplastic self-consistent FLD prediction model and its application for austenitic and ferritic stainless steels}}
+  {Metals and Materials International}
+  {In Press}
+  {
+  }
+
   % ---------------------------------------------------------

### 2020-04-16 mycv/subs/papers.tex
typo

--- 2018-12-26 mycv/subs/papers.tex
@@
   % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}}
+  {An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}
+  {}
+  {Submitted for publication}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, D Steglich}
+  {Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}
+  {International Journal of Mechanical Sciences}
+  {Accepted for publication}
+  {
+  }
+
+  % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
+  {\href{https://doi.org/10.1088/1361-651X/ab4b66}{Extension of the VPSC model to account for elasto-visco-plastic behavior using a perturbed viscoplastic approach}}
+  {Modelling and Simulation in Materials Science and Engineering}
+  {Vol. 27(8) 085013, 2019}
+  {
+  }
+
+  % ---------------------------------------------------------
+  \cventry
+  {S. J. Park, \underline{Y. Jeong}, C. W. Kim, J. H. Lee, S. C. Cho, S. B. Lee, S. K. Lee, D. H. Kim, H. U. Hong$^*$}
+  {\href{https://doi.org/10.1016/j.msea.2019.138260}{Superior tensile fracture strength of hot isostatically pressed TiC–steel metallic composite fabricated by a novel infiltration}}
+  {Materials Science and Engineering: A}
+  {Vol. 764(9), 2019}
+  {
+  }
+
+  % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, Timo Manninen}
+  {\href{https://doi.org/10.1007/s12540-019-00292-5}{Enhancement in viscoplastic self-consistent FLD prediction model and its application for austenitic and ferritic stainless steels}}
+  {Metals and Materials International}
+  {Vol. 25(6) pp1548-1563, 2019}
+  {
+  }
+
   % ---------------------------------------------------------

### 2020-06-29 mycv/subs/papers.tex
Updates in diffraction.ipynb

@@
 \begin{cventries}
+  % % ---------------------------------------------------------
+  % \cventry
+  % {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
+  % {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
+  % {}
+  % {in preparation}
+  % {
+  % }
   % ---------------------------------------------------------
@@
   {An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}
-  {}
-  {Submitted for publication}
+  {International Journal of Plasticity}
+  {In Press}
   {
@@
   {\underline{Y. Jeong}$^*$, D Steglich}
-  {Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}
+  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
   {International Journal of Mechanical Sciences}
-  {Accepted for publication}
+  {Vol. 181, 105680, 2020}
   {

### 2020-06-29 mycv/subs/skills.tex
Updates
Updates in diffraction.ipynb

@@
   {Digital Image Correlation (DIC)}
-  {VIC3D}
+  {VIC3D, DICE}
 
@@
   {Computer skills}
-  {Linux, Git, Abaqus (UMAT and Python script), Parallel computation}
+  {Linux, Git, Parallel computation}
 
   \cvskill
-  {Constutitive modelling}
-  {Macro-mechanical description for anisotropic metals using anisotropic yield functions}
+  {Constitutive modelling}
+  {Macro-mechanical description on anisotropic metals using anisotropic yield functions}
 
@@
   {Crystal plasticity}
-  {Viscoplastic self-consistent (VPSC) and Elasto-viscoplastic self-consistent crystal plasticity models}
+  {Visco-plastic / Elasto-visco-plastic self-consistent crystal plasticity models}
 

### 2020-07-20 mycv/subs/papers.tex
Edits

@@
   \cventry
-  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}}
-  {An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}
+  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
+  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
   {International Journal of Plasticity}
-  {In Press}
+  {Available Online}
   {
@@
   \cventry
-  {\underline{Y. Jeong}$^*$, D Steglich}
+  {\underline{Y. Jeong}$^*$, D. Steglich}
   {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
@@
   \cventry
-  {\underline{Y. Jeong}$^*$, F. Barlat, C. Tom\'{e}, W. Wen}
+  {\underline{Y. Jeong}$^*$, F. Barlat, C. N. Tom\'{e}, W. Wen}
   {\href{http://dx.doi.org/10.1016/j.ijplas.2016.07.015}{A comparative study between micro- and macro-mechanical constitutive models developed for complex loading scenarios}}
@@
   \cventry
-  {F. Barlat, \underline{Y. Jeong}, J. Ha, C Tom\'{e}, Myoung-Gyu Lee, W. Wen}
+  {F. Barlat, \underline{Y. Jeong}, J. Ha, C. N. Tom\'{e}, M.-G. Lee, W. Wen}
   {\href{https://dx.doi.org/10.4028/www.scientific.net/KEM.725.3}{Advances in Constitutive Modeling of Plasticity for Forming Applications}}
@@
   \cventry
-  {\underline{Y. Jeong}, F. Barlat, C. Tom\'{e}, W. Wen}
+  {\underline{Y. Jeong}, F. Barlat, C. N. Tom\'{e}, W. Wen}
   {\href{http://dx.doi.org/10.1063/1.4963544}{Validation of Homogeneous Anisotropic Hardening Approach Based on Crystal Plasticity}}

### 2020-11-25 mycv/subs/papers.tex
Updates in paper

@@
 \begin{cventries}
-  % % ---------------------------------------------------------
-  % \cventry
-  % {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
-  % {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
-  % {}
-  % {in preparation}
-  % {
-  % }
+  % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
+  {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
+  {}
+  {in preparation}
+  {
+  }
   % ---------------------------------------------------------
@@
   {International Journal of Plasticity}
-  {Available Online}
+  {Vol. 135, 102812, 2020}
   {

### 2021-08-18 mycv/subs/papers.tex
update

@@
   \cventry
-  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
-  {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
-  {}
-  {in preparation}
+  {\underline{Y. Jeong}$^*$, B. Jeon, C N. Tom\'{e}}
+  {Finite element analysis using an incremental elasto-visco-plastic self-consistent polycrystal model: FE simulations on Zr and low-carbon steel subjected to bending, stress-relaxation, and unloading}
+  {submitted to International Journal of Plasticity}
+  {Under review}
   {

### 2021-12-15 mycv/subs/papers.tex
update

--- 2020-11-25 mycv/subs/papers.tex
@@
   \cventry
-  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
-  {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
-  {}
-  {in preparation}
+  {\underline{Y. Jeong}$^*$, B. Jeon, C N. Tom\'{e}}
+  {\href{https://doi.org/10.1016/j.ijplas.2021.103110}{Finite element analysis using an incremental elasto-visco-plastic self-consistent polycrystal model: FE simulations on Zr and low-carbon steel subjected to bending, stress-relaxation, and unloading}}
+  {International Journal of Plasticity}
+  {Vol. 147, 103110, 2021}
   {

### 2022-05-13 mycv/subs/papers.tex
snapshot

--- 2020-11-25 mycv/subs/papers.tex
@@
   \cventry
-  {\underline{Y. Jeong}$^*$, C N. Tom\'{e}, B. Jeon}
-  {Finite element analysis of incremental elasto-visco-plastic self-consistent polycrystal model}
-  {}
-  {in preparation}
-  {
-  }
-  % ---------------------------------------------------------
-  \cventry
   {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
-  {\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto-visco-plastic self-consistent formulation: Application to steel subjected to loading path changes}}
-  {International Journal of Plasticity}
-  {Vol. 135, 102812, 2020}
-  {
-  }
-  % ---------------------------------------------------------
-  \cventry
-  {\underline{Y. Jeong}$^*$, D. Steglich}
-  {\href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}}
-  {International Journal of Mechanical Sciences}
-  {Vol. 181, 105680, 2020}
-  {
-  }
-
-  % ---------------------------------------------------------
-  \cventry
-  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
-  {\href{https://doi.org/10.1088/1361-651X/ab4b66}{Extension of the VPSC model to account for elasto-visco-plastic behavior using a perturbed viscoplastic approach}}
+  {Extension of the VPSC model to account for elasto-visco-plastic behavior using a perturbed viscoplastic approach}
   {Modelling and Simulation in Materials Science and Engineering}
-  {Vol. 27(8) 085013, 2019}
+  {Vol. 27(8), 2019}
   {
@@
   {\underline{Y. Jeong}$^*$, Timo Manninen}
-  {\href{https://doi.org/10.1007/s12540-019-00292-5}{Enhancement in viscoplastic self-consistent FLD prediction model and its application for austenitic and ferritic stainless steels}}
+  {\href{10.1007/s12540-019-00292-5}{Enhancement in viscoplastic self-consistent FLD prediction model and its application for austenitic and ferritic stainless steels}}
   {Metals and Materials International}
-  {Vol. 25(6) pp1548-1563, 2019}
+  {Vol. 25(6), 2019}
   {
@@
   \cventry
-  {\underline{Y. Jeong}$^*$, F. Barlat, C. N. Tom\'{e}, W. Wen}
+  {\underline{Y. Jeong}$^*$, F. Barlat, C. Tom\'{e}, W. Wen}
   {\href{http://dx.doi.org/10.1016/j.ijplas.2016.07.015}{A comparative study between micro- and macro-mechanical constitutive models developed for complex loading scenarios}}
@@
   \cventry
-  {F. Barlat, \underline{Y. Jeong}, J. Ha, C. N. Tom\'{e}, M.-G. Lee, W. Wen}
+  {F. Barlat, \underline{Y. Jeong}, J. Ha, C Tom\'{e}, Myoung-Gyu Lee, W. Wen}
   {\href{https://dx.doi.org/10.4028/www.scientific.net/KEM.725.3}{Advances in Constitutive Modeling of Plasticity for Forming Applications}}
@@
   \cventry
-  {\underline{Y. Jeong}, F. Barlat, C. N. Tom\'{e}, W. Wen}
+  {\underline{Y. Jeong}, F. Barlat, C. Tom\'{e}, W. Wen}
   {\href{http://dx.doi.org/10.1063/1.4963544}{Validation of Homogeneous Anisotropic Hardening Approach Based on Crystal Plasticity}}

### 2022-05-13 mycv/subs/papers.tex

--- 2021-12-15 mycv/subs/papers.tex
@@
 \begin{cventries}
+  % ---------------------------------------------------------
+  \cventry
+  {B. Jeon, M.-S. Kim, S. Choi, \underline{Y. Jeong}$^*$}
+  {\href{}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
+  {in preparation}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {M. Joo, M.-S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C N. Tom\'{e}, B. Jeon, \underline{Y. Jeong}$^*$}
+  {\href{}{A case study of crystal plasticity finite element analysis for springback prediction: the effect of prestrain on springback}}
+  {Submitted}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {J. Park, \underline{Y. Jeong}$^*$}
+  {\href{}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}}
+  {Submitted}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {M.S. Lee, T. Kawasaki, T. Yamashita, S. Harjo, Y.T. Hyun, \underline{Y. Jeong}, T. S. Jun$^*$}
+  {\href{https://doi.org/10.1038/s41598-022-07640-3}{In-situ neutron diffraction study of lattice deformation behaviour of commercially pure titanium at cryogenic temperature}}
+  {Scientific Reports}
+  {Vol. 12 (1), 1-10, 2022}
+  {
+  }
   % ---------------------------------------------------------

### 2022-05-20 mycv/subs/papers.tex
updates

@@
   {\href{}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}}
-  {Submitted}
-  {}
+  {Korean Journal of Metals and Materials}
+  {Accepted}
   {

### 2022-08-10 mycv/subs/papers.tex
update

--- 2022-05-13 mycv/subs/papers.tex
@@
   {\href{}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
-  {in preparation}
+  {Submitted}
   {}
@@
   {J. Park, \underline{Y. Jeong}$^*$}
-  {\href{}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}}
-  {Submitted}
-  {}
+  {\href{http://dx.doi.org/10.3365/KJMM.2022.60.8.607}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}}
+  {Korean Journal of Metals and Materials}
+  {Vol. 60 (8), 607-618, 2022}
   {

### 2022-10-04 mycv/subs/papers.tex
IJMS paper has been accepted
updates

@@
   {M. Joo, M.-S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C N. Tom\'{e}, B. Jeon, \underline{Y. Jeong}$^*$}
-  {\href{}{A case study of crystal plasticity finite element analysis for springback prediction: the effect of prestrain on springback}}
-  {Submitted}
+  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback   }}
+  {In press}
   {}

### 2022-10-17 mycv/subs/papers.tex
updates in papers

@@
   {\href{}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
-  {Submitted}
-  {}
+  {Journal of Magnesium and Alloys}
+  {Accepted}
   {

### 2022-11-01 mycv/subs/papers.tex
updates

@@
   {M. Joo, M.-S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C N. Tom\'{e}, B. Jeon, \underline{Y. Jeong}$^*$}
-  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback   }}
+  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback}}
+  {International Journal of Mechanical Sciences}
   {In press}
-  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {Lalit Kauschik, Ki-Seong Park, Jeong-Gyun Kim, Jae-Seong Lee, Youngung Jeong, Shi-Hoon Choi$^*$}
+  {\href{https://doi.org/10.1016/j.ijplas.2022.103467}{Reconstructing orientation data from the images of IPF maps and ODF sections extracted from the literature: A data-collection method for machine learning}}
+  {International Journal of Plasticity}
+  {Vol. 159, 103467, 2022}
   {

### 2023-06-02 mycv/subs/papers.tex
updates in paper

--- 2022-10-04 mycv/subs/papers.tex
@@
   {B. Jeon, M.-S. Kim, S. Choi, \underline{Y. Jeong}$^*$}
-  {\href{}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
-  {Submitted}
-  {}
+  {\href{https://doi.org/10.1016/j.jma.2022.10.017}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
+  {Journal of Magnesium and Alloys}
+  {Vol. 11(4), p1393-1407, 2023}
   {
@@
   {M. Joo, M.-S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C N. Tom\'{e}, B. Jeon, \underline{Y. Jeong}$^*$}
-  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback   }}
-  {In press}
-  {}
+  {\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback}}
+  {International Journal of Mechanical Sciences}
+  {Vol. 237, 107796, 2023}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {Lalit Kauschik, Ki-Seong Park, Jeong-Gyun Kim, Jae-Seong Lee, \underline{Youngung Jeong}, Shi-Hoon Choi$^*$}
+  {\href{https://doi.org/10.1016/j.ijplas.2022.103467}{Reconstructing orientation data from the images of IPF maps and ODF sections extracted from the literature: A data-collection method for machine learning}}
+  {International Journal of Plasticity}
+  {Vol. 159, 103467, 2022}
   {

### 2023-10-10 mycv/subs/papers.tex
updates in papers

--- 2022-10-17 mycv/subs/papers.tex
@@
   % ---------------------------------------------------------
+
+  % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
+  {Thermal ratcheting of uranium simulated by a thermo-elasto-visco-plastic self-consistent polycrystal model}
+  {submitted}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {B. Jeon, S.-Y. Lee, J. Lee, \underline{Y. Jeong}$^*$}
+  {Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}
+  {in preparation}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {B. Jeon, M.-S. Lee, T.-S. Jun, \underline{Y. Jeong}$^*$}
+  {Temperature-dependent behavior of CP-Ti interpreted via self-consistent crystal plasticity simulation}
+  {submitted}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
   \cventry
   {B. Jeon, M.-S. Kim, S. Choi, \underline{Y. Jeong}$^*$}
-  {\href{}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
+  {\href{https://doi.org/10.1016/j.jma.2022.10.017}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}}
   {Journal of Magnesium and Alloys}
-  {Accepted}
+  {Vol. 11(4), p1393-1407, 2023}
   {
@@
 \begin{cventries}
+
+\item
   % ---------------------------------------------------------
-\item
+  \cventry
+  {Carlos N. Tome$^*$, \underline{Y. Jeong}}
+  {\href{https://doi.org/10.1007/978-3-031-40920-2_68}{Thermal Ratcheting of Uranium Simulated with a Thermo-Elasto-Visco-Plastic Polycrystal Model}}
+  {Proceedings of the 14th International Conference on the Technology of Plasticity - Current Trends in the Technology of Plasticity}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {B. Jeon, \underline{Y. Jeong}$^*$}
+  {\href{https://doi.org/10.1007/978-3-031-40920-2_69}{Interpretation of the Unloading Non-linearity in Dual-Phase 980 Steel Using an Elasto-Visco-Plastic Self-consistent Polycrystal Model}}
+  {Proceedings of the 14th International Conference on the Technology of Plasticity - Current Trends in the Technology of Plasticity}
+  {}
+  {
+  }
+
+  % ---------------------------------------------------------
   \cventry

### 2024-03-25 mycv/subs/fundings.tex
snapshot

--- 2018-05-24 mycv/subs/fundings.tex
@@
   \cvhonor
+  {자동차용 경량소재 가상공학 플랫폼 구축}
+  {}
+  {\href{http://www.motie.go.kr/www/main.do}{South Korean Ministry of Trade, Industry and Energy}}
+  {2018-2021}
+
+  \cvhonor
+  {Technology development for flame retardant eco hybrid composites}
+  {}
+  {NSF of Korea}
+  {2018-2027}
+
+  \cvhonor
   {Multi-scale crystal plasticity framework for multiphase metals under non-linear forming scenario} %Award
-  {NRF-2017R1D1A1B03031052}%EVENT
-  {National Science Foundation of Korea} %Location
+  {책임; NRF-2017R1D1A1B03031052}%EVENT
+  {NSF of Korea} %Location
   {2017-2020} %dates

### 2024-03-25 mycv/subs/papers.tex
snapshot

@@
   \cventry
+  {Jos\'{e} Victoria-Hern\'{a}ndez, \underline{Y. Jeong}$^*$, Dietmar Letzig}
+  {Deformation mechanisms of Mg-ZEWK2000 alloy at RT and 225°C studied by slip trace analysis and interpreted via crystal plasticity simulations}
+  {submitted}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
   {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
   {Thermal ratcheting of uranium simulated by a thermo-elasto-visco-plastic self-consistent polycrystal model}
+  {submitted}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {G. R. Peterson, \underline{Y. Jeong}, C. N. Tom\'{e}, M. D. Sangid$^*$}
+  {Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}
+  {submitted}
+  {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {Jaeseong Lee, Dirk Steglich, \underline{Y. Jeong}$^*$}
+  {Crystal plasticity finite element simulations on extruded Mg-10Gd rod with texture gradient}
   {submitted}
@@
   {B. Jeon, M.-S. Lee, T.-S. Jun, \underline{Y. Jeong}$^*$}
-  {Temperature-dependent behavior of CP-Ti interpreted via self-consistent crystal plasticity simulation}
-  {submitted}
-  {}
+  {\href{https://doi.org/10.1016/j.msea.2023.145904}{Temperature-dependent behavior of CP-Ti interpreted via self-consistent crystal plasticity simulation}}
+  {Materials Science and Engineering: A}
+  {Vol. 890, 149504, 2024}
   {

### 2024-05-21 mycv/subs/papers.tex
Status changes in papers
snapshot

@@
   \cventry
-  {Jos\'{e} Victoria-Hern\'{a}ndez, \underline{Y. Jeong}$^*$, Dietmar Letzig}
+  {Jos\'{e} Victoria-Hern\'{a}ndez$^*$, \underline{Y. Jeong}$^*$, Dietmar Letzig}
   {Deformation mechanisms of Mg-ZEWK2000 alloy at RT and 225°C studied by slip trace analysis and interpreted via crystal plasticity simulations}
-  {submitted}
-  {}
-  {
-  }
-  % ---------------------------------------------------------
-  \cventry
-  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
-  {Thermal ratcheting of uranium simulated by a thermo-elasto-visco-plastic self-consistent polycrystal model}
-  {submitted}
+  {in preparation}
   {}
@@
   {Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}
-  {in preparation}
+  {submitted}
   {}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {\underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
+  {\href{https://doi.org/10.1016/j.jnucmat.2024.155159}{Thermal ratcheting of uranium simulated by a thermo-elasto-visco-plastic self-consistent polycrystal model}}
+  {Journal of Nuclear Materials}
+  {Vol. 597, 155159, 2024}
   {
@@
   \cventry
+  {D. Steglich, \underline{Y. Jeong}, M. O. Andar}
+  {\href{https://doi.org/10.21741/9781644903131-121}{Insights from crystal-plasticity-based predictions on deformation of an Mg-10Gd extrudate}}
+  {Materials Research Proceedings, Proceedings of ESAFORM2024}
+  {Vol 41, 2024}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
   {Carlos N. Tome$^*$, \underline{Y. Jeong}}

### 2024-08-23 mycv/subs/papers.tex
updates in the status of Cermet paper
Updates

@@
   \cventry
-  {G. R. Peterson, \underline{Y. Jeong}, C. N. Tom\'{e}, M. D. Sangid$^*$}
-  {Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}
-  {submitted}
-  {}
-  {
-  }
-  % ---------------------------------------------------------
-  \cventry
   {Jaeseong Lee, Dirk Steglich, \underline{Y. Jeong}$^*$}
   {Crystal plasticity finite element simulations on extruded Mg-10Gd rod with texture gradient}
-  {submitted}
-  {}
+  {Journal of Magnesium and Alloys}
+  {Accepted}
   {
@@
   {Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}
-  {submitted}
-  {}
+  {International Journal of Plasticity}
+  {in-press}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {G. R. Peterson, \underline{Y. Jeong}, C. N. Tom\'{e}, M. D. Sangid$^*$}
+  {\ref{https://doi.org/10.1016/j.ijplas.2024.104032}{Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}}
+  {International Journal of Plasticity}
+  {Vol. 179, 104032, 2024}
   {

### 2024-08-26 mycv/subs/papers.tex
Updates

@@
   {B. Jeon, S.-Y. Lee, J. Lee, \underline{Y. Jeong}$^*$}
-  {Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}
+  {\ref{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}}
   {International Journal of Plasticity}
-  {in-press}
+  {Vol. 181, 104098, 2024}
   {

### 2024-08-30 mycv/subs/papers.tex
snapshot

--- 2024-05-21 mycv/subs/papers.tex
@@
   \cventry
-  {G. R. Peterson, \underline{Y. Jeong}, C. N. Tom\'{e}, M. D. Sangid$^*$}
-  {Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}
-  {submitted}
+  {B. Jeon, C. N. Tom\'{e}, \underline{Y. Jeong}$^*$}
+  {A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}
+  {in preparation}
   {}
@@
   {Jaeseong Lee, Dirk Steglich, \underline{Y. Jeong}$^*$}
-  {Crystal plasticity finite element simulations on extruded Mg-10Gd rod with texture gradient}
-  {submitted}
-  {}
+  {\href{https://doi.org/10.1016/j.jma.2024.08.009}{Crystal plasticity finite element simulations on extruded Mg-10Gd rod with texture gradient}}
+  {Journal of Magnesium and Alloys}
+  {in-press}
   {
@@
   {B. Jeon, S.-Y. Lee, J. Lee, \underline{Y. Jeong}$^*$}
-  {Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}
-  {submitted}
-  {}
+  {\href{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto-viscoplastic self-consistent crystal plasticity model to U-draw bending and springback of dual-phase high strength steel}}
+  {International Journal of Plasticity}
+  {Vol. 181, 104098, 2024}
+  {
+  }
+  % ---------------------------------------------------------
+  \cventry
+  {G. R. Peterson, \underline{Y. Jeong}, C. N. Tom\'{e}, M. D. Sangid$^*$}
+  {\href{https://doi.org/10.1016/j.ijplas.2024.104032}{Cermet design through modeling the thermal cyclic stability via a Temperature- dependent, Incremental Elasto-Viscoplastic, Self-Consistent (TE-VPSC) formulation}}
+  {International Journal of Plasticity}
+  {Vol. 179, 104032, 2024}
   {

### 2024-10-21 mycv/subs/papers.tex
update
updates in the list of my papers in preparation
snapshot

@@
 \begin{cventries}
-  % ---------------------------------------------------------
-
+  % % ---------------------------------------------------------
+  % \cventry
+  % {Jos\'{e} Victoria-Hern\'{a}ndez$^*$, \underline{Y. Jeong}$^*$, Dietmar Letzig}
+  % {Deformation mechanisms of Mg-ZEWK2000 alloy at RT and 225°C studied by slip trace analysis and interpreted via crystal plasticity simulations}
+  % {in preparation}
+  % {}
+  % {
+  % }
   % ---------------------------------------------------------
   \cventry
-  {Jos\'{e} Victoria-Hern\'{a}ndez$^*$, \underline{Y. Jeong}$^*$, Dietmar Letzig}
-  {Deformation mechanisms of Mg-ZEWK2000 alloy at RT and 225°C studied by slip trace analysis and interpreted via crystal plasticity simulations}
-  {in preparation}
+  {B. Jeon, C. N. Tom\'{e}, \underline{Y. Jeong}$^*$}
+  {\href{https://dx.doi.org/10.2139/ssrn.4969819)}{A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}}
+  {submitted}
   {}
@@
   }
-  % ---------------------------------------------------------
+    %% % ---------------------------------------------------------
   \cventry
-  {B. Jeon, C. N. Tom\'{e}, \underline{Y. Jeong}$^*$}
-  {A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}
-  {in preparation}
+  {Iftekhar A. Riyad, Bjorn Clausen, Daniel J. Savage, \underline{Y. Jeong}, Donald W. Brown, Mark Knezevic}
+  {Modeling deformation, recovery, and recrystallization of tantalum using a higher order elasto-viscoplastic self-consistent model}
+  {submitted}
   {}
@@
   {Journal of Magnesium and Alloys}
-  {in-press}
+  {Vol. 12 (8), 3409-3430, 2024}
   {

### 2024-11-07 mycv/subs/papers.tex
Updates in papers
Indicated the corresponding author of JMPS paper
updates in papers

@@
   \cventry
-  {B. Jeon, C. N. Tom\'{e}, \underline{Y. Jeong}$^*$}
-  {\href{https://dx.doi.org/10.2139/ssrn.4969819)}{A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}}
-  {submitted}
-  {}
+  {B. Jeon, \underline{Y. Jeong}$^*$, C. N. Tom\'{e}}
+  {\href{https://doi.org/10.1016/j.jmrt.2024.11.043}{A critical discussion of elasto-visco-plastic self-consistent (EVPSC) models}}
+  {Journal of Materials Research and Technology}
+  {In press}
   {
@@
   \cventry
-  {Iftekhar A. Riyad, Bjorn Clausen, Daniel J. Savage, \underline{Y. Jeong}, Donald W. Brown, Mark Knezevic}
+  {Iftekhar A. Riyad, Bjorn Clausen, Daniel J. Savage, \underline{Y. Jeong}, Donald W. Brown, Mark Knezevic$^*$}
   {Modeling deformation, recovery, and recrystallization of tantalum using a higher order elasto-viscoplastic self-consistent model}
-  {submitted}
-  {}
+  {Journal of Mechanics and Physics of Solids}
+  {Vol. 194, 105925, 2025}
   {

### 2025-03-14 mycv/mylatex_cv.tex
My Latex cv has been uploaded

\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot, % set margins without considering header and footer
    top=2 cm, % seperation between body and page edge from the top
    bottom=2 cm, % seperation between body and page edge from the bottom
    left=2 cm, % seperation between body and page edge from the left
    right=2 cm, % seperation between body and page edge from the right
    footskip=1.0 cm, % seperation between body and footer
    % showframe % for debugging
]{geometry} % for adjusting page geometry
\usepackage{titlesec} % for customizing section titles
\usepackage{tabularx} % for making tables with fixed width columns
\usepackage{array} % tabularx requires this
\usepackage[dvipsnames]{xcolor} % for coloring text
\definecolor{primaryColor}{RGB}{0, 0, 0} % define primary color
\usepackage{enumitem} % for customizing lists
\usepackage{fontawesome5} % for using icons
\usepackage{amsmath} % for math
\usepackage[
    pdftitle={John Doe's CV},
    pdfauthor={John Doe},
    pdfcreator={LaTeX with RenderCV},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref} % for links, metadata and bookmarks
\usepackage[pscoord]{eso-pic} % for floating text on the page
\usepackage{calc} % for calculating lengths
\usepackage{bookmark} % for bookmarks
\usepackage{lastpage} % for getting the total number of pages
\usepackage{changepage} % for one column entries (adjustwidth environment)
\usepackage{paracol} % for two and three column entries
\usepackage{ifthen} % for conditional statements
\usepackage{needspace} % for avoiding page brake right after the section title
\usepackage{iftex} % check if engine is pdflatex, xetex or luatex

% Ensure that generate pdf is machine readable/ATS parsable:
\ifPDFTeX
    \input{glyphtounicode}
    \pdfgentounicode=1
    \usepackage[T1]{fontenc}
    \usepackage[utf8]{inputenc}
    \usepackage{lmodern}
\fi

\usepackage{charter}

% Some settings:
\raggedright
\AtBeginEnvironment{adjustwidth}{\partopsep0pt} % remove space before adjustwidth environment
\pagestyle{empty} % no header or footer
\setcounter{secnumdepth}{0} % no section numbering
\setlength{\parindent}{0pt} % no indentation
\setlength{\topskip}{0pt} % no top skip
\setlength{\columnsep}{0.15cm} % set column seperation
\pagenumbering{gobble} % no page numbering

\titleformat{\section}{\needspace{4\baselineskip}\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule]

\titlespacing{\section}{
    % left space:
    -1pt
}{
    % top space:
    0.3 cm
}{
    % bottom space:
    0.2 cm
} % section title spacing

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$} % custom bullet points
\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0 cm + 10pt
    ]
}{
    \end{itemize}
} % new environment for highlights

\newenvironment{highlightsforbulletentries}{
    \begin{itemize}[
        topsep=0.10 cm,
        parsep=0.10 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=10pt
    ]
}{
    \end{itemize}
} % new environment for highlights for bullet entries

\newenvironment{onecolentry}{
    \begin{adjustwidth}{
        0 cm + 0.00001 cm
    }{
        0 cm + 0.00001 cm
    }
}{
    \end{adjustwidth}
} % new environment for one column entries

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5 cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
} % new environment for two column entries

\newenvironment{threecolentry}[3][]{
    \onecolentry
    \def\thirdColumn{#3}
    \setcolumnwidth{, \fill, 4.5 cm}
    \begin{paracol}{3}
    {\raggedright #2} \switchcolumn
}{
    \switchcolumn \raggedleft \thirdColumn
    \end{paracol}
    \endonecolentry
} % new environment for three column entries

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\linespread{1.5}
}{
    \par\kern\topsep
} % new environment for the header

\newcommand{\placelastupdatedtext}{% \placetextbox{<horizontal pos>}{<vertical pos>}{<stuff>}
  \AddToShipoutPictureFG*{% Add <stuff> to current page foreground
    \put(
        \LenToUnit{\paperwidth-2 cm-0 cm+0.05cm},
        \LenToUnit{\paperheight-1.0 cm}
    ){\vtop{{\null}\makebox[0pt][c]{
        \small\color{gray}\textit{Last updated in September 2024}\hspace{\widthof{Last updated in September 2024}}
    }}}%
  }%
}%

% save the original href command in a new command:
\let\hrefWithoutArrow\href

% new command for external links:

\begin{document}
    \newcommand{\AND}{\unskip
        \cleaders\copy\ANDbox\hskip\wd\ANDbox
        \ignorespaces
    }
    \newsavebox\ANDbox
    \sbox\ANDbox{$|$}

    \begin{header}
        \fontsize{25 pt}{25 pt}\selectfont Youngung Jeong

        \vspace{5 pt}

        \normalsize
        \mbox{Your Location}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{mailto:yjeong@changwon.ac.kr}{yjeong@changwon.ac.kr}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{tel:+82-55-214-3694}{+82-55-214-3694}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://youngung.github.io/}{youngung.github.io}}%
        \kern 5.0 pt%
        \AND%
        %\kern 5.0 pt%
        %\mbox{\hrefWithoutArrow{https://linkedin.com/in/yourusername}{linkedin.com/in/yourusername}}%
        \kern 5.0 pt%
        \AND%
        \kern 5.0 pt%
        \mbox{\hrefWithoutArrow{https://github.com/youngung}{github.com/youngung}}%
    \end{header}

    \vspace{5 pt - 0.3 cm}

%    \section{Welcome to RenderCV!}
%        \begin{onecolentry}
%            \href{https://rendercv.com}{RenderCV} is a LaTeX-based CV/resume version-control and maintenance app. It allows you to create a high-quality CV or resume as a PDF file from a YAML file, with \textbf{Markdown syntax support} and \textbf{complete control over the LaTeX code}.
%        \end{onecolentry}
%        \vspace{0.2 cm}
%        \begin{onecolentry}
%            The boilerplate content was inspired by \href{https://github.com/dnl-blkv/mcdowell-cv}{Gayle McDowell}.
%        \end{onecolentry}
%    \section{Quick Guide}
%    \begin{onecolentry}
%        \begin{highlightsforbulletentries}
%        \item Each section title is arbitrary and each section contains a list of entries.
%        \item There are 7 unique entry types: \textit{BulletEntry}, \textit{TextEntry}, \textit{EducationEntry}, \textit{ExperienceEntry}, \textit{NormalEntry}, \textit{PublicationEntry}, and \textit{OneLineEntry}.
%        \item Select a section title, pick an entry type, and start writing your section!
%        \item \href{https://docs.rendercv.com/user_guide/}{Here}, you can find a comprehensive user guide for RenderCV.
%        \end{highlightsforbulletentries}
%    \end{onecolentry}

    \section{Education}
        \begin{twocolentry}{Mar 2001 – Feb 2008}
            \textbf{Hanyang University}, BS, Department of Materials Science and Engineering
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Mar 2008 – Feb 2010}
            \textbf{POSTECH}, MS, GIFT
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Mar 2008 – Feb 2010}
            \textbf{POSTECH}, PhD, GIFT
        \end{twocolentry}
        \vspace{0.10 cm}
    \section{Experience}
        \begin{twocolentry}{Mar 2017 – Present}
            \textbf{Assistant, Associate professor}, Changwon National University, Republic of Korea
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{July 2024 – Aug 2024}
            \textbf{Short term visitor}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Feb 2022 – Feb 2024}
            \textbf{Guest Scientist (offsite)}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Dec 2016 – Feb 2017}
            \textbf{Postdoc}, POSTECH, Republic of Korea
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{twocolentry}{Mar 2016 – Nov 2016}
            \textbf{Research Scientist}, Clemson university, SC, USA
        \end{twocolentry}
        \begin{twocolentry}{Mar 2014 – Feb 2016}
            \textbf{Postdoc}, NIST, MD, USA
        \end{twocolentry}
        \begin{twocolentry}{Apr 2012 – Sep 2012}
            \textbf{Research Affiliate}, Los Alamos National Laboratory, NM, USA
        \end{twocolentry}
        \begin{twocolentry}{June 2011 – Dec 2011}
            \textbf{Guest Researcher}, NIST, MD, USA
        \end{twocolentry}
        \vspace{0.10 cm}

%        \begin{twocolentry}{
%            June 2003 – Aug 2003
%        }
%            \textbf{Software Engineer Intern}, Microsoft -- Redmond, WA\end{twocolentry}

%        \vspace{0.10 cm}
%        \begin{onecolentry}
%            \begin{highlights}
%                \item Designed a UI for the VS open file switcher (Ctrl-Tab) and extended it to tool windows
%                \item Created a service to provide gradient across VS and VS add-ins, optimizing its performance via caching
%                \item Built an app to compute the similarity of all methods in a codebase, reducing the time from $\mathcal{O}(n^2)$ to $\mathcal{O}(n \log n)$
%                \item Created a test case generation tool that creates random XML docs from XML Schema
%                \item Automated the extraction and processing of large datasets from legacy systems using SQL and Perl scripts
%            \end{highlights}
%        \end{onecolentry}

    \section{Selected recent publications}
        \begin{samepage}
            \begin{twocolentry}{2024}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.jmrt.2024.11.043}{A critical discussion of elasto‑visco‑plastic self‑consistent (EVPSC) models}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                \mbox{B. Jeon}, \mbox{\textbf{\textit{Y. Jeong}}}, \mbox{C. N. Tomé}
            \end{onecolentry}
            \begin{onecolentry}
                Journal of Materials Research Technology
            \end{onecolentry}
            \vspace{0.10 cm}

            \begin{twocolentry}{2024}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto‑viscoplastic self‑consistent crystal plasticity model to U‑draw bending and springback of dual‑phase high strength steel}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                \mbox{B. Jeon}, \mbox{S.-Y. Lee}, \mbox{J. Lee}, \mbox{\textbf{\textit{Y. Jeong}}}
            \end{onecolentry}
            \begin{onecolentry}
                \mbox{International Journal of Plasticity}
            \end{onecolentry}
            \vspace{0.10 cm}

            \begin{twocolentry}{2023}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                \mbox{M. Joo}, \mbox{M. -S. Wi}, \mbox{S.-Y. Yoon}, \mbox{S.-Y. Lee}, \mbox{F. Barlat}, \mbox{C. N. Tomé}, \mbox{B. Jeon}, \mbox{C. N. Tomé}, \mbox{\textbf{\textit{Y. Jeong}}},
             \end{onecolentry}
             \begin{onecolentry}
               \mbox{International Journal of Mechanical Sciences}
             \end{onecolentry}
            \vspace{0.10 cm}

            \begin{twocolentry}{2021}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.ijplas.2021.103110}{Finite element analysis using an incremental elasto‑visco‑plastic self‑consistent polycrystal model: FE simulations on Zr and low‑carbon steel subjected to bending, stress‑relaxation, and unloading}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                \mbox{\textbf{\textit{Y. Jeong}}}, \mbox{B. Jeon}, \mbox{C. N. Tomé}
            \end{onecolentry}
            \begin{onecolentry}
                \mbox{International Journal of Plasticity}
            \end{onecolentry}
            \vspace{0.10 cm}

            \begin{twocolentry}{2020}
                \begin{highlights}
                \item\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto‑visco‑plastic self‑consistent formulation: Application to steel subjected to loading path changes}
                \end{highlights}
            \end{twocolentry}
            \begin{onecolentry}
                \mbox{\textbf{\textit{Y. Jeong}}}, \mbox{C. N. Tomé}
            \end{onecolentry}
            \begin{onecolentry}
                \mbox{ International Journal of Plasticity}
            \end{onecolentry}
            \vspace{0.10 cm}

        \end{samepage}

    \section{GitHub repositories}
        \begin{twocolentry}{\href{https://github.com/youngung/evpsc}{github.com/youngung/evpsc}}\textbf{Elasto-visco-plastic self-consistent model} (private repo)
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{onecolentry}
            \begin{highlights}
                \item Extended visco-plastic self-consistent model to account for elasticity
                \item Offer both stand-alone and FE-interface simulation capabilities
                \item Written primarily in Fortran with Python and shell scripts.
                \item Finite element simulation via user material interface of Abaqus/standard solver
            \end{highlights}
        \end{onecolentry}

        \vspace{0.2 cm}
        \begin{twocolentry}{\href{https://github.com/youngung/texture3}{github.com/youngung/texture3}}
            \textbf{In-house Python scripts for texture analysis}
        \end{twocolentry}
        \vspace{0.10 cm}
        \begin{onecolentry}
            \begin{highlights}
                \item Contoured pole figures for discrete orientations used in VPSC-like crystal plasticity codes
                \item Written entirely in Python with open-sourced libraries including matplotlib, NumPy and SciPy
            \end{highlights}
        \end{onecolentry}

    \section{Skills}
        \begin{onecolentry}
            Fortran, Python (NumPy, SciPy, and matplotlib), Matlab, shell scripts, Git
        \end{onecolentry}
\end{document}

### 2025-03-14 mycv/mylatex_cv.tex
minor edits

@@
         \normalsize
-        \mbox{Your Location}%
+        \mbox{School of Materials Science and Engineering, Changwon National University}%
         \kern 5.0 pt%
@@
         \mbox{\hrefWithoutArrow{https://youngung.github.io/}{youngung.github.io}}%
-        \kern 5.0 pt%
-        \AND%
-        %\kern 5.0 pt%
-        %\mbox{\hrefWithoutArrow{https://linkedin.com/in/yourusername}{linkedin.com/in/yourusername}}%
         \kern 5.0 pt%
@@
         \begin{twocolentry}{Mar 2008 – Feb 2010}
-            \textbf{POSTECH}, MS, GIFT
+            \textbf{POSTECH}, MS, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
         \end{twocolentry}
@@
         \begin{twocolentry}{Mar 2008 – Feb 2010}
-            \textbf{POSTECH}, PhD, GIFT
+            \textbf{POSTECH}, PhD, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
         \end{twocolentry}
@@
         \begin{twocolentry}{Mar 2017 – Present}
-            \textbf{Assistant, Associate professor}, Changwon National University, Republic of Korea
+            \textbf{Assistant, associate professor}, Changwon National University, ROK
         \end{twocolentry}
@@
         \begin{twocolentry}{Dec 2016 – Feb 2017}
-            \textbf{Postdoc}, POSTECH, Republic of Korea
+            \textbf{Postdoc}, POSTECH, ROK
         \end{twocolentry}
@@
         \end{twocolentry}
+        \vspace{0.10 cm}
         \begin{twocolentry}{Mar 2014 – Feb 2016}
@@
         \end{twocolentry}
+        \vspace{0.10 cm}
         \begin{twocolentry}{Apr 2012 – Sep 2012}
@@
         \end{twocolentry}
+        \vspace{0.10 cm}
         \begin{twocolentry}{June 2011 – Dec 2011}

### 2025-03-16 mycv/mylatex_cv.tex
snapshot of latex cv

@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{Mar 2008 – Feb 2010}
+        \begin{twocolentry}{Mar 2010 – Feb 2014}
             \textbf{POSTECH}, PhD, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
@@
         \vspace{0.10 cm}
+
     \section{Experience}
@@
                 \begin{highlights}
-                \item\href{https://doi.org/10.1016/j.jmrt.2024.11.043}{A critical discussion of elasto‑visco‑plastic self‑consistent (EVPSC) models}
-                \end{highlights}
-            \end{twocolentry}
-            \begin{onecolentry}
-                \mbox{B. Jeon}, \mbox{\textbf{\textit{Y. Jeong}}}, \mbox{C. N. Tomé}
-            \end{onecolentry}
-            \begin{onecolentry}
-                Journal of Materials Research Technology
-            \end{onecolentry}
-            \vspace{0.10 cm}
-
-            \begin{twocolentry}{2024}
-                \begin{highlights}
                 \item\href{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto‑viscoplastic self‑consistent crystal plasticity model to U‑draw bending and springback of dual‑phase high strength steel}
@@
             \begin{onecolentry}
-                \mbox{B. Jeon}, \mbox{S.-Y. Lee}, \mbox{J. Lee}, \mbox{\textbf{\textit{Y. Jeong}}}
+                {\it International Journal of Plasticity} 181
             \end{onecolentry}
             \begin{onecolentry}
-                \mbox{International Journal of Plasticity}
+                B. Jeon, S.-Y. Lee, J. Lee, {\underline{\textit{Y. Jeong}*}}
             \end{onecolentry}
@@
             \begin{onecolentry}
-                \mbox{M. Joo}, \mbox{M. -S. Wi}, \mbox{S.-Y. Yoon}, \mbox{S.-Y. Lee}, \mbox{F. Barlat}, \mbox{C. N. Tomé}, \mbox{B. Jeon}, \mbox{C. N. Tomé}, \mbox{\textbf{\textit{Y. Jeong}}},
+                {\it International Journal of Mechanical Sciences} 237
               \end{onecolentry}
             \begin{onecolentry}
-               \mbox{International Journal of Mechanical Sciences}
+                M. Joo, M. -S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C. N. Tomé, B. Jeon, {\underline{\textit{Y. Jeong}*}},
              \end{onecolentry}
@@
             \begin{onecolentry}
-                \mbox{\textbf{\textit{Y. Jeong}}}, \mbox{B. Jeon}, \mbox{C. N. Tomé}
+                {\it International Journal of Plasticity} 147
             \end{onecolentry}
             \begin{onecolentry}
-                \mbox{International Journal of Plasticity}
+                \mbox{\underline{\textit{Y. Jeong}*}}, \mbox{B. Jeon}, \mbox{C. N. Tomé}
             \end{onecolentry}
@@
             \begin{onecolentry}
-                \mbox{\textbf{\textit{Y. Jeong}}}, \mbox{C. N. Tomé}
+                {\it International Journal of Plasticity} 135
             \end{onecolentry}
             \begin{onecolentry}
-                \mbox{ International Journal of Plasticity}
+                {\underline{\textit{Y. Jeong}*}}, C. N. Tomé
             \end{onecolentry}
             \vspace{0.10 cm}
+        \end{samepage}
 
-        \end{samepage}
+        \section{Goverment-funded projects}
+        \begin{twocolentry}{2023 - 2027}
+            \textbf{Mid-career Researcher Program (PI), National Research Foundation of Korea}
+        \end{twocolentry}
+        \vspace{0.10 cm}
+        \begin{twocolentry}{2020 - 2027}
+            \textbf{BK21, National Research Foundation of Korea}
+        \end{twocolentry}
+        \vspace{0.10 cm}
+        \begin{twocolentry}{2018 - 2024}
+            \textbf{Engieering Research Center, National Research Foundation of Korea}
+        \end{twocolentry}
+        \vspace{0.10 cm}
+        \begin{twocolentry}{2020 - 2023}
+            \textbf{General Research Program (PI), National Research Foundation of Korea}
+        \end{twocolentry}
+        \vspace{0.10 cm}
+        \begin{twocolentry}{2018 - 2020}
+            \textbf{Virtual engineering platform project, Ministry of Trade, Industry and Energy}
+        \end{twocolentry}
+        \vspace{0.10 cm}
+        \begin{twocolentry}{2017 - 2020}
+            \textbf{General Research Program (PI), National Research Foundation of Korea}
+        \end{twocolentry}
+
+    \section{Skills}
+        \begin{onecolentry}
+            \item Constitutive modeling: Phenomenological plasticity and crystal plasticity modeling
+            \item Programming languages: Fortran, Python (NumPy, SciPy, and matplotlib), Matlab, shell scripts
+            \item Languages: Korean, English
+            \item Experimental Mechanics: Uniaxial tension, shear, hydraulic bulge test, biaxial tests
+            \item Diffraction experiments: X-ray diffraction, Electron back-scattered diffraction and analysis
+            \item Computer skills: Linux, Git
+        \end{onecolentry}
 
@@
             \begin{highlights}
-                \item Extended visco-plastic self-consistent model to account for elasticity
-                \item Offer both stand-alone and FE-interface simulation capabilities
-                \item Written primarily in Fortran with Python and shell scripts.
-                \item Finite element simulation via user material interface of Abaqus/standard solver
+                \item Extended visco-plastic self-consistent model to account for elasticity ($\Delta$EVPSC and $\sigma$EVPSC)
+                \item Stand-alone calculation capabilities
+                \item Various example shell and python scripts as well as Jupyter notebook files
+                \item User material subroutine (UMAT) of Abaqus/standard solver
+                \item Written primarily in Fortran with Python and shell scripts
+            \end{highlights}
+        \end{onecolentry}
+        \vspace{0.4 cm}
+
+        \begin{twocolentry}{\href{https://github.com/Jeonbohye/VPSC8-dEVPSC}{github.com/Jeonbohye/VPSC8-dEVPSC}}\textbf{VPSC8 and EVPSC} (private repo)
+        \end{twocolentry}
+        \begin{onecolentry}
+            \begin{highlights}
+                \item Combines VPSC8 and EVPSC models
+                \item Numerical implementation of VPSC, $\Delta$EVPSC, and $\sigma$EVPSC constitutive model
+                \item Three separate build commands for executables of VPSC8, $\Delta$EVPSC, and $\sigma$EVPSC.
             \end{highlights}
@@
 
-        \vspace{0.2 cm}
+        \vspace{0.4 cm}
         \begin{twocolentry}{\href{https://github.com/youngung/texture3}{github.com/youngung/texture3}}
@@
         \end{twocolentry}
-        \vspace{0.10 cm}
         \begin{onecolentry}
             \begin{highlights}
-                \item Contoured pole figures for discrete orientations used in VPSC-like crystal plasticity codes
+                \item Can plot pole figures of discrete orientations used in VPSC-like crystal plasticity codes
                 \item Written entirely in Python with open-sourced libraries including matplotlib, NumPy and SciPy
@@
         \end{onecolentry}
+        \vspace{0.2 cm}
+        \section{Misc.}
+        \begin{twocolentry}{2023-present}
+            \begin{highlights}
+                \item Board member of Korean Society for Technology of Plasticity
+            \end{highlights}
+        \end{twocolentry}
+        \vspace{0.2 cm}
+        \begin{twocolentry}{2019-present}
+            \begin{highlights}
+                \item Editoiral board member of Korean Journal of Metals and Materials
+            \end{highlights}
+        \end{twocolentry}
+    \vspace{0.2 cm}
+    \newpage
+    \section{Full list of publications}
+    \begin{enumerate}
+        \item
+        \begin{twocolentry}{submitted}
+            \href{}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
+        \end{twocolentry}
+        %\begin{onecolentry}
+        %    {\it }
+        %\end{onecolentry}
+        \begin{onecolentry}
+            José Victoria-Hernández, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
+        \end{onecolentry}
+        \vspace{0.10 cm}
 
-    \section{Skills}
+        \item
+        \begin{twocolentry}{2025}
+            \href{https://doi.org/10.1016/j.jmps.2024.105925}{Modeling deformation, recovery, and recrystallization of tantalum using a higher order elasto-viscoplastic self-consistent model}
+        \end{twocolentry}
         \begin{onecolentry}
-            Fortran, Python (NumPy, SciPy, and matplotlib), Matlab, shell scripts, Git
+            {\it Journal of the Mechanics and Physics of Solids}, 194, 105925
         \end{onecolentry}
+        \begin{onecolentry}
+            I. A. Riyad, B. Clausen, D. J. Savage, {\underline{\textit{Y. Jeong}}}, D. W. Brown, M. Knezevic*
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2024}
+            \href{https://doi.org/10.1016/j.jmrt.2024.11.043}{A critical discussion of elasto‑visco‑plastic self‑consistent (EVPSC) models}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Journal of Materials Research Technology}, 33, 7596-7609
+        \end{onecolentry}
+        \begin{onecolentry}
+            B. Jeon, {\underline{\textit{Y. Jeong}*}}, C. N. Tomé
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2024}
+            \href{https://doi.org/10.1016/j.ijplas.2024.104098}{Direct application of elasto‑viscoplastic self‑consistent crystal plasticity model to U‑draw bending and springback of dual‑phase high strength steel}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Plasticity}, 181, 104098
+        \end{onecolentry}
+        \begin{onecolentry}
+            Bohye Jeon, Shin-Yeong Lee, Jinwoo Lee, {\underline{\textit{Youngung Jeong}*}}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2024}
+            \href{https://doi.org/10.1016/j.jnucmat.2024.155159}{Thermal ratcheting of uranium simulated with a thermo-elasto-visco-plastic self-consistent polycrystal model}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Journal of Nuclear Materials}, 597, 155159
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Youngung Jeong}*}}, Carlos N. Tomé
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2024}
+            \href{https://doi.org/10.1016/j.jma.2024.08.009}{Crystal plasticity finite element simulations on extruded Mg-10Gd rod with texture gradient}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Journal of Magnesium and Alloys}, 12 , 3409-3430
+        \end{onecolentry}
+        \begin{onecolentry}
+            Jaeseong Lee, Dirk Steglich, {\underline{\textit{Youngung Jeong}*}}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2024}
+            \href{https://doi.org/10.1016/j.ijplas.2024.104032}{A comprehensive analysis of cermet design and thermal cyclic stability via elasto-viscoplastic crystal plasticity modeling}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Plasticity}, 179, 104032
+        \end{onecolentry}
+        \begin{onecolentry}
+            Glenn R Peterson, {\underline{\textit{Youngung Jeong}}}, Carlos N Tomé, Michael D Sangid*
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2024}
+            \href{https://doi.org/10.1016/j.msea.2023.145904}{Temperature-dependent behavior of CP-Ti interpreted via self-consistent crystal plasticity simulation}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Materials Science and Engineering: A}, 890, 145904
+        \end{onecolentry}
+        \begin{onecolentry}
+            Bohye Jeon, Min-Su Lee, Tea-Sung Jun, {\underline{\textit{Youngung Jeong}*}}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2023}
+            \href{https://doi.org/10.1016/j.jma.2022.10.017}{Finite element analysis using elasto-visco-plastic self-consistent polycrystal model for E-form Mg sheet subjected to bending}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Journal of Magnesium and Alloys}, 11, 1393-1407
+        \end{onecolentry}
+        \begin{onecolentry}
+            B. Jeon, M. S. Kim, S. H. Choi, {\underline{\textit{Y. Jeong}*}}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2023}
+            \href{https://doi.org/10.1016/j.ijmecsci.2022.107796}{A crystal plasticity finite element analysis on the effect of prestrain on springback}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Mechanical Sciences} 237, 107796
+        \end{onecolentry}
+        \begin{onecolentry}
+            M. Joo, M. -S. Wi, S.-Y. Yoon, S.-Y. Lee, F. Barlat, C. N. Tomé, B. Jeon, {\underline{\textit{Y. Jeong}*}}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2023}
+            \href{https://doi.org/10.1016/j.ijplas.2022.103467}{Reconstructing orientation data from the images of IPF maps and ODF sections extracted from the literature: A data-collection method for machine learning}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Plasticity}, 159, 103467
+        \end{onecolentry}
+        \begin{onecolentry}
+            L. Kaushik, K.-S. Park, J.-G. Kim, J. Lee, {\underline{\textit{Y. Jeong}}}, S.-H. Choi*
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2022}
+            \href{http://dx.doi.org/10.3365/KJMM.2022.60.8.607}{Prediction and validation of stress triaxiality assisted by elasto-visco-plastic polycrystal model}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Korean Journal of Metals and Materials}, 60, 607-618
+        \end{onecolentry}
+        \begin{onecolentry}
+            Jinhwa Park, {\underline{\textit{Youngung Jeong}*}}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2022}
+            \href{https://doi.org/10.1038/s41598-022-07640-3}{In-situ neutron diffraction study of lattice deformation behaviour of commercially pure titanium at cryogenic temperature}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Scientific Reports}, 12, 3719
+        \end{onecolentry}
+        \begin{onecolentry}
+            M.-S. Lee, T. Kawasaki, T. Yamashita, S. Harjo, Y.-T. Hyun, {\underline{\textit{Y. Jeong}}}, T.-S. Jun
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2021}
+            \href{https://doi.org/10.1016/j.ijplas.2021.103110}{Finite element analysis using an incremental elasto‑visco‑plastic self‑consistent polycrystal model: FE simulations on Zr and low‑carbon steel subjected to bending, stress‑relaxation, and unloading}
+        \end{twocolentry}
+        \begin{onecolentry}
+            \it{International Journal of Plasticity}, 147, 103110
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, \mbox{B. Jeon}, \mbox{C. N. Tomé}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2020}
+            \href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto‑visco‑plastic self‑consistent formulation: Application to steel subjected to loading path changes}
+        \end{twocolentry}
+        \begin{onecolentry}
+            \it{International Journal of Plasticity}, 135, 102812
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, \mbox{C. N. Tomé}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2020}
+            \href{https://doi.org/10.1016/j.ijmecsci.2020.105680}{Modelling-assisted description of anisotropic edge failure in magnesium sheet alloy under mixed-mode loading}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Mechanical Sciences}, 181, 105680
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, Dirk Steglich
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2019}
+            \href{https://doi.org/10.1088/1361-651X/ab4b66}{Extension of the VPSC model to account for elasto‑visco‑plastic behavior using a
+            perturbed viscoplastic approach}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Modelling and Simulation in Materials Science and Engineering}, 27, 085013
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, C. N. Tomé
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2019}
+            \href{https://doi.org/10.1016/j.msea.2019.138260}{Superior tensile fracture strength of hot isostatically pressed TiC–steel metallic composite fabricated by a novel infiltration}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Materials Science and Engineering: A}, 764, 138260
+        \end{onecolentry}
+        \begin{onecolentry}
+            S. J. Park, {\underline{\textit{Y. Jeong}}}, C. W. Kim, J. H. Lee, S. C. Cho, S. B. Lee, S. K. Lee, D. H. Kim, H. U. Hong*
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2019}
+            \href{https://doi.org/10.1007/s12540-019-00292-5}{Enhancement in viscoplastic self-consistent FLD prediction model and its application for austenitic and ferritic stainless steels}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Metals and Materials International}, 25, 1548–1563
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, T. Manninen
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2018}
+            \href{https://doi.org/10.1016/j.ijplas.2018.07.010}{A crystal plasticity model for describing the anisotropic hardening behavior of steel
+            sheets during strain‑path changes }
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Plasticity},
+        \end{onecolentry}
+        \begin{onecolentry}
+            H. Kim, F. Barlat, Y. Lee, S. Zaman, C. S. Lee, {\underline{\textit{Y. Jeong}*}}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2017}
+            \href{http://dx.doi.org/10.1016/j.ijplas.2016.07.015}{A comparative study between micro‑ and macro‑mechanical constitutive models developed for complex loading scenarios }
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Plasticity}, 93, 212‑228
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, F. Barlat, C. N. Tomé, W. Wen
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2016}
+            \href{https://doi.org/10.1107/S1600576716013662}{Uncertainty in flow stress measurements using X‑ray diffraction for sheet metals subjected to large plastic deformations}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Journal of Applied Crystallography}, 49, 1991‑2004
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, T. Gnäupel‑Herold, M. Iadicola, A. Creuziger
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2016}
+            \href{http://dx.doi.org/10.1016/j.ijmecsci.2016.08.013}{Texture‑based forming limit prediction for Mg sheet alloys ZE10 and AZ31 }
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Mechanical Sciences}, 117, 102‑114
+        \end{onecolentry}
+        \begin{onecolentry}
+            D. Steglich, {\underline{\textit{Y. Jeong}*}}
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2016}
+            \href{http://dx.doi.org/10.1088/0965-0393/24/5/055005}{Forming limit prediction using a self‑consistent crystal plasticity framework: a case study for BCC fiber textures}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Modelling and Simulation in Materials Science and Engineering}, 24, 055002
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, M.‑S. Pham, M. Iaidocola, A. Creuziger, T. Foecke
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2016}
+            \href{http://dx.doi.org/10.1016/j.actamat.2016.04.013}{Multiaxial constitutive behavior of an interstitial‑free steel: measurements through X‑ray and digital image correlation }
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Acta Materialia}, 112, 84‑93
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}},  M. Iaidocola, T. Gnäupel‑Herold, A. Creuziger
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2016}
+            \href{http://dx.doi.org/10.1016/j.msea.2015.09.108}{Effect of martensitic phase transformation on the behavior of 304 austenitic stainless steel under tension}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Materials Science and Engineering: A}, 649, 174‑183
+        \end{onecolentry}
+        \begin{onecolentry}
+            H. Wang*, {\underline{\textit{Y. Jeong}*}}, B. Calusen, Y. LiU, R. J. McCabe, F. Barlat, C. N. Tomé
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2015}
+            \href{http://dx.doi.org/10.1016/j.ijplas.2014.06.009}{Evaluation of biaxial flow stress based on Elasto‑Viscoplastic Self‑Consistent analysis of X‑ray Diffraction Measurements}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Plasticity}, 66, 103‑118
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}}}, T. Gnaupel-Herold, F. Barlat, M. Iadicola, A. Creuziger, M.‑G. Lee*
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2012}
+            \href{http://dx.doi.org/10.1088/0965-0393/20/2/024009}{Application of crystal plasticity to an austenitic stainless steel }
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it Modelling and Simulation in Materials Science and Engineering}, 20, 024009
+        \end{onecolentry}
+        \begin{onecolentry}
+            {\underline{\textit{Y. Jeong}*}}, F. Barlat, M.-G. Lee
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+        \item
+        \begin{twocolentry}{2012}
+            \href{http://dx.doi.org/10.1016/j.ijsolstr.2012.06.017}{Biaxial Deformation Behavior of AZ31 Magnesium Alloy: Crystal‑Plasticity‑Based Prediction and Experimental Validation}
+        \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Solids and Structure}, 49, 3551‑3561
+        \end{onecolentry}
+        \begin{onecolentry}
+            D. Steglich*, {\underline{\textit{Y. Jeong}}}, M. O. Andar, T. Kuwabara
+        \end{onecolentry}
+        \vspace{0.10 cm}
+
+    \end{enumerate}
+
 \end{document}

### 2025-03-17 mycv/mylatex_cv.tex
snapshot

@@
     \section{Education}
-        \begin{twocolentry}{Mar 2001 – Feb 2008}
+        \begin{twocolentry}{03/01/2001 – 02/29/2008}
             \textbf{Hanyang University}, BS, Department of Materials Science and Engineering
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{Mar 2008 – Feb 2010}
+        \begin{twocolentry}{03/01/2008 – 02/28/2010}
             \textbf{POSTECH}, MS, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{Mar 2010 – Feb 2014}
+        \begin{twocolentry}{03/01/2010 – 02/28/2014}
             \textbf{POSTECH}, PhD, Graduate Institute of Ferrous Technology (supervisor: F. Barlat)
@@
     \section{Experience}
-        \begin{twocolentry}{Mar 2017 – Present}
+        \begin{twocolentry}{03/01/2017 – Present}
             \textbf{Assistant, associate professor}, Changwon National University, ROK
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{July 2024 – Aug 2024}
+        \begin{twocolentry}{07/11/2024 – 08/16/2024}
             \textbf{Short term visitor}, Los Alamos National Laboratory, NM, USA
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{Feb 2022 – Feb 2024}
+        \begin{twocolentry}{02/01/2022 – 02/1/2024}
             \textbf{Guest Scientist (offsite)}, Los Alamos National Laboratory, NM, USA
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{Dec 2016 – Feb 2017}
+        \begin{twocolentry}{12/01/2016 – 02/28/2017}
             \textbf{Postdoc}, POSTECH, ROK
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{Mar 2016 – Nov 2016}
+        \begin{twocolentry}{03/01/2016 – 11/30/2016}
             \textbf{Research Scientist}, Clemson university, SC, USA
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{Mar 2014 – Feb 2016}
+        \begin{twocolentry}{03/01/2014 – 02/29/2016}
             \textbf{Postdoc}, NIST, MD, USA
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{Apr 2012 – Sep 2012}
+        \begin{twocolentry}{04/01/2012 – 09/30/2012}
             \textbf{Research Affiliate}, Los Alamos National Laboratory, NM, USA
@@
         \vspace{0.10 cm}
-        \begin{twocolentry}{June 2011 – Dec 2011}
+        \begin{twocolentry}{06/01/2011 – 12/31/2011}
             \textbf{Guest Researcher}, NIST, MD, USA
@@
             \item Languages: Korean, English
-            \item Experimental Mechanics: Uniaxial tension, shear, hydraulic bulge test, biaxial tests
-            \item Diffraction experiments: X-ray diffraction, Electron back-scattered diffraction and analysis
+            \item Experimental Mechanics: uniaxial tension, shear, hydraulic bulge test, biaxial tests, digital image correlation (DIC)
+            \item Diffraction experiments: X-ray diffraction, Electron back-scattered diffraction (EBSD), Residual stress analysis
             \item Computer skills: Linux, Git
@@
         \end{onecolentry}
+        \vspace{0.4 cm}
 
-        \vspace{0.4 cm}
         \begin{twocolentry}{\href{https://github.com/youngung/texture3}{github.com/youngung/texture3}}
@@
             \begin{highlights}
-                \item Can plot pole figures of discrete orientations used in VPSC-like crystal plasticity codes
+                \item Can plot contoured pole figures and inverse pole figures from discrete orientations
                 \item Written entirely in Python with open-sourced libraries including matplotlib, NumPy and SciPy
+                \item Can generate RGB maps of EBSD (electron basck-scattered diffraction) scans
             \end{highlights}
         \end{onecolentry}
-        \vspace{0.2 cm}
+        \vspace{0.4 cm}
+
         \section{Misc.}
@@
         \begin{onecolentry}
-            José Victoria-Hernández, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
+            José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
         \end{onecolentry}

### 2025-04-18 mycv/cv_latex.tex
updates

--- 2025-03-17 mycv/mylatex_cv.tex
@@
         \begin{enumerate}
+
+        \item
+          \begin{twocolentry}{in preparation}
+            \href{}{Deformation mechanism and texture evolution in AZ31 Mg alloy under uniaxial compression: experiments and simulations}
+          \end{twocolentry}
+          \begin{onecolentry}
+            Jongbin Go*,  {\underline{\textit{Y. Jeong}*}}, Myeong-heom Park*, Sangwon Lee, Si Gao, Nobuhiro Tsuji
+          \end{onecolentry}
+          \vspace{0.10 cm}
+
+        \item
+          \begin{twocolentry}{in preparation}
+            \href{}{Reverse engineering material behavior using Bayesian inference and finite element analysis on ring-pull test}
+          \end{twocolentry}
+          \begin{onecolentry}
+            B. Jeon, C. N. Tome, P. M. Beck, B. Eftinik, A. Talapatra, {\underline{\textit{Y. Jeong}*}}, L. Capolungo*
+          \end{onecolentry}
+          \vspace{0.10 cm}
+
         \item
@@
         \end{twocolentry}
-        %\begin{onecolentry}
-        %    {\it }
-        %\end{onecolentry}
         \begin{onecolentry}

### 2025-06-05 mycv/cv_latex.tex
Addition of Abrar's manuscript
paper status updates
updates

@@
         \item
-          \begin{twocolentry}{in preparation}
+          \begin{twocolentry}{submitted}
+            \href{}{Leveraging Machine Learning and Crystal Plasticity for Efficient Calibration of Yld2004-18p Anisotorpic Yield Function}
+          \end{twocolentry}
+          \begin{onecolentry}
+            A. S. Ebrahim,  J. Kim, {\underline{\textit{Y. Jeong}}}, T. Park, H. Lim, B. L. Kinsey, J. Ha*
+          \end{onecolentry}
+          \vspace{0.10 cm}
+
+        \item
+          \begin{twocolentry}{submitted}
             \href{}{Deformation mechanism and texture evolution in AZ31 Mg alloy under uniaxial compression: experiments and simulations}
@@
         \item
-          \begin{twocolentry}{in preparation}
+          \begin{twocolentry}{submitted}
             \href{}{Reverse engineering material behavior using Bayesian inference and finite element analysis on ring-pull test}
@@
         \item
-          \begin{twocolentry}{submitted}
-            \href{}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
+          \begin{twocolentry}{Accepted}
+            \href{https://doi.org/10.1016/j.ijplas.2025.104380}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
         \end{twocolentry}
+        \begin{onecolentry}
+            {\it International Journal of Plasticity}, in press
+        \end{onecolentry}
         \begin{onecolentry}

### 2025-08-05 mycv/cv_latex.tex
update

@@
         \normalsize
-        \mbox{School of Materials Science and Engineering, Changwon National University}%
+        \mbox{Department of Materials Science and Metallurgy, Changwon National University}%
         \kern 5.0 pt%
@@
     \begin{samepage}
+
+            \begin{twocolentry}{2025}
+                \begin{highlights}
+                \item\href{https://doi.org/10.1016/j.ijplas.2025.104380}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
+                \end{highlights}
+            \end{twocolentry}
+            \begin{onecolentry}
+                {\it International Journal of Plasticity} 191
+            \end{onecolentry}
+            \begin{onecolentry}
+              José Victoria-Hernández*, {\underline{\textit{Y. Jeong}*}}, Dietmar Letzig
+            \end{onecolentry}
+            \vspace{0.10 cm}
+
             \begin{twocolentry}{2024}
@@
 
-            \begin{twocolentry}{2020}
-                \begin{highlights}
-                \item\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto‑visco‑plastic self‑consistent formulation: Application to steel subjected to loading path changes}
-                \end{highlights}
-            \end{twocolentry}
-            \begin{onecolentry}
-                {\it International Journal of Plasticity} 135
-            \end{onecolentry}
-            \begin{onecolentry}
-                {\underline{\textit{Y. Jeong}*}}, C. N. Tomé
-            \end{onecolentry}
-            \vspace{0.10 cm}
+            % \begin{twocolentry}{2020}
+            %     \begin{highlights}
+            %     \item\href{https://doi.org/10.1016/j.ijplas.2020.102812}{An efficient elasto‑visco‑plastic self‑consistent formulation: Application to steel subjected to loading path changes}
+            %     \end{highlights}
+            % \end{twocolentry}
+            % \begin{onecolentry}
+            %     {\it International Journal of Plasticity} 135
+            % \end{onecolentry}
+            % \begin{onecolentry}
+            %     {\underline{\textit{Y. Jeong}*}}, C. N. Tomé
+            % \end{onecolentry}
+            % \vspace{0.10 cm}
+
         \end{samepage}
@@
             \item Constitutive modeling: Phenomenological plasticity and crystal plasticity modeling
+            \item Languages: Korean, English
+            \item Computer skills: Linux, Git
             \item Programming languages: Fortran, Python (NumPy, SciPy, and matplotlib), Matlab, shell scripts
-            \item Languages: Korean, English
             \item Experimental Mechanics: uniaxial tension, shear, hydraulic bulge test, biaxial tests, digital image correlation (DIC)
             \item Diffraction experiments: X-ray diffraction, Electron back-scattered diffraction (EBSD), Residual stress analysis
-            \item Computer skills: Linux, Git
         \end{onecolentry}
@@
         \item
-          \begin{twocolentry}{Accepted}
+          \begin{twocolentry}{2025}
             \href{https://doi.org/10.1016/j.ijplas.2025.104380}{Role of recovery in the microstructure development and mechanical behavior of a ductile Mg-Zn-Nd-Y-Zr alloy: an analysis using EBSD data and crystal plasticity simulations}
@@
         \begin{onecolentry}
-            {\it International Journal of Plasticity}, in press
+            {\it International Journal of Plasticity}, 191, 104380
         \end{onecolentry}

### 2025-08-05 mycv/cv_latex.tex
update

@@
         \kern 5.0 pt%
-        \mbox{\hrefWithoutArrow{https://youngung.github.io/}{youngung.github.io}}%
+        \mbox{\hrefWithoutArrow{https://youngung.github.io/}{https://youngung.github.io}}%
         \kern 5.0 pt%
@@
         \kern 5.0 pt%
-        \mbox{\hrefWithoutArrow{https://github.com/youngung}{github.com/youngung}}%
+        \mbox{\hrefWithoutArrow{https://github.com/youngung}{https://github.com/youngung}}%
     \end{header}
@@
         \begin{twocolentry}{2018 - 2024}
-            \textbf{Engieering Research Center, National Research Foundation of Korea}
+            \textbf{Engineering Research Center, National Research Foundation of Korea}
         \end{twocolentry}
